---
title: "Agglomeration Final"
author: "Nikhil Kalathil"
date: "2024-05-14"
output: html_document
---

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warnings = FALSE)
```

```{r, include = FALSE}
#Libraries
library(tigris)
library(tidyverse)
library(here)
library(leaflet)
library(ggrepel)
library(RColorBrewer)
library(grid)
library(gridExtra)
library(cowplot)
library(readxl)
library(janitor)
library(geofacet)
library(jsonlite)
library(ggridges)
library(sf)
library(here)
library(patchwork)
library(plotly)
library(leaflet.extras)
library(units)
library(jtools)
library(urbnmapr)
library(DescTools)


set.seed(37)
title_theme <- theme(axis.text = element_text(size = 14), 
        axis.title = element_text(size = 18), 
        title = element_text(size = 20))

axis_theme <- theme(axis.text = element_text(size = 10), 
        axis.title = element_text(size = 18), 
         strip.text.x = element_text(size = 16))
```

```{r, include = FALSE}
#Area Crosswalks
area_codes <- readRDS(here("State Data/area_crosswalk.RDS")) %>% 
  mutate(area_title = str_remove(area_title, " -- Statewide")) %>% 
  mutate(area_fips = case_when(
    nchar(area_fips) == 4 ~ paste("0", area_fips, sep = ""), 
    TRUE ~ area_fips
  ))

states <- data.frame(state_abbr = state.abb, area_title = state.name)

area_codes <- left_join(area_codes, states) %>% 
  mutate(state_abbr = case_when(
    area_title == "District of Columbia" ~ "DC",
    area_title == "Puerto Rico" ~ "PR",
    TRUE ~ state_abbr))
```


```{r}
ExpandColorsLIGHT <- function(colors, n, steps = 11){
  if(n <= steps){
    suppressWarnings({
      sapply(colors, function(x){colorRampPalette(c(x, "#FFFFFF"))(steps)}) %>% 
        as.data.frame() %>% 
        filter(row_number() <= n) %>% 
        gather(key = original.color, value = expanded.color)
    })
  }else{
    warning("Select n < steps!")
  }
}
```


```{r}
ExpandColorsDARK <- function(colors, n, steps = 11){
  if(n <= steps){
    suppressWarnings({
      sapply(colors, function(x){colorRampPalette(c(x, "#000000"))(steps)}) %>% 
        as.data.frame() %>% 
        filter(row_number() <= n) %>% 
        gather(key = original.color, value = expanded.color)
    })
  }else{
    warning("Select n < steps!")
  }
}
```

```{r, include = FALSE}
#Map Data
county_sf <- counties(cb = TRUE) %>% 
  shift_geometry(position = "outside")
states_sf <- states(cb = TRUE, resolution = "20m") %>%
  shift_geometry(position = "outside")
```

```{r, include = FALSE}
#Change projection of data for leaflet
states_leaflet <- states_sf %>% 
  sf::st_transform('+proj=longlat +datum=WGS84')

counties_leaflet <- county_sf %>% 
  sf::st_transform('+proj=longlat +datum=WGS84') 
```

```{r, include = FALSE}
#Convert county data to a table
county_data <- counties_leaflet %>% 
  as_tibble() %>% 
  select(STATEFP, COUNTYFP, AFFGEOID) %>% 
  mutate(area_fips = paste(STATEFP, COUNTYFP, sep = ""), 
         st = as.numeric(STATEFP))
```


```{r, include = FALSE}
#Get center of each county
county_centers <- counties_leaflet %>% 
  filter(str_detect(NAME, "Mariana", negate = TRUE)) %>% 
  st_centroid() %>% 
  sf::st_transform('+proj=longlat +datum=WGS84')
```

```{r, include = FALSE}
#Load Existing Data
qcew_3digits <- readRDS(here("State Data/qcew_3digit.RDS")) %>% 
  mutate(industry_desc = substring(industry_title, 11))
```

```{r, include = FALSE}
#Simplify to get industry codes
ind_3digit <- qcew_3digits %>% 
  select(naics_3digit = ind_code, naics_3digit_label = industry_desc) %>% 
  distinct() %>% 
  arrange(naics_3digit_label)
```

```{r, include = FALSE}
#Define colors 
emp_ind_vector <- c(brewer.pal(9, "Greys")[4], "#cf4633", "#BEAED4", "#a8e4a0", "#FDBF6F",  "#386CB0", "#FB8072", brewer.pal(9, "Greys")[3], brewer.pal(9, "Greys")[8], "#80B1D3", "#F0027F",  "#4DAF4A", "#F1E2CC", "#6A3D9A", "#E78AC3", "#CBD5E8", "#666666", brewer.pal(9, "Greys")[5],  brewer.pal(9, "Greys")[6], "#A65628", brewer.pal(9, "Greys")[7])
```

```{r}
#create data frame mapping colors to industries
col_map <- data.frame(ind_3digit$naics_3digit_label, emp_ind_vector)
```

```{r}
rd_col <- data.frame(ind_3digit.naics_3digit_label = "Scientific R&D", emp_ind_vector = "#8DD3C7")
```

```{r}
col_map <- bind_rows(col_map, rd_col)
```


```{r}
# Map 3-digit NAICS to 3-digit Colors
get_col_vec <- function(data){ 
  data %>% 
    select(naics_3digit_label) %>% 
    distinct() %>% 
    unlist()
  }
```

```{r}
#Function to get appropriate 3-digit colors
get_col_match <- function(data){ 
  
 col_vec <- get_col_vec(data)
 
 col_out <- col_map %>% 
   filter(ind_3digit.naics_3digit_label %in% col_vec) %>% 
   select(emp_ind_vector) %>% 
   unlist() %>% 
   unname()
 
  return(col_out)
  
}
```

```{r}
#Get County GEOIDS and crosswalks
cbp_geoid <- read.csv(here("County Data/5_digit_naics_2019.csv")) %>% 
  mutate(area_fips = str_sub(GEO_ID, -5)) %>% 
  select(GEO_ID, NAME, area_fips) %>% distinct()

cbp_empzes <- read.csv(here("County Data/5_digit_naics_2019.csv")) %>% 
  select(EMPSZES_LABEL, EMPSZES) %>% 
  distinct()

cbp_io <- readRDS(here("Input Output Data/cbp_manf_IO_crosswalk.RDS")) 
```


```{r, include = FALSE}
#read county-level manufacturing data
cbp_2019 <- read.csv(here("County Data/6_digit_naics_CBP.csv")) %>% 
  left_join(cbp_geoid) %>% 
  left_join(county_data) %>% 
  left_join(area_codes %>% select(st, state_abbr)) %>% 
  mutate(across(.cols = c(EMP, ESTAB, PAYANN), ~ gsub(",", "", .)),
    emp_num = as.numeric(EMP), 
    ESTAB = as.numeric(ESTAB), 
    mean_pay = as.numeric(PAYANN)
    ) %>% 
  filter(str_detect(NAME, "Mariana", negate = TRUE)) %>% 
  left_join(cbp_empzes)
```


```{r}
cbp_2019_all <- read.csv(here("County Data/total_naics_2019.csv")) %>% 
  mutate(across(.cols = c(EMP, ESTAB, PAYANN), ~ gsub(",", "", .)),
    tot_emp = as.numeric(EMP), 
    tot_estab = as.numeric(ESTAB), 
    tot_mean_earnings = as.numeric(PAYANN)) %>% 
  filter(str_detect(NAME, "Mariana", negate = TRUE), EMPSZES_LABEL == "All establishments") %>% 
  mutate(geo_merge = NAME) %>% 
  left_join(counties_leaflet %>% 
              mutate(geo_merge = paste(NAMELSAD, STATE_NAME, sep = ", ")) %>% 
              rename(county_name = NAME))
```

```{r}
cbp_all <- cbp_2019_all %>% select(county_tot_emp = tot_emp, county_tot_estabs = tot_estab, NAME)
```

```{r}
cbp_pay <- cbp_2019 %>% 
  filter(EMPSZES == 1) %>% 
  left_join(cbp_io) %>% 
  ungroup() %>% 
  group_by(ind_code) %>% 
  reframe(ind_mean_pay = mean(mean_pay)) %>% 
  ungroup() 
```


```{r}
#read Input Output Data
use_table_final <- readRDS(here("Input Output Data/use_table_final.RDS"))
sup_com_agg <- readRDS(here("Input Output Data/sup_com_agg.RDS"))
ind_agg <- readRDS(here("Input Output Data/ind_agg.RDS"))
com_agg <- readRDS(here("Input Output Data/com_agg.RDS"))
supply_table_final <- readRDS(here("Input Output Data/supply_table_final.RDS"))
```

```{r}
ind_crosswalk <- readRDS(here("Input Output Data/ind_crosswalk.RDS"))
```



```{r}
#Read NAICS Codes
naics_codes <- read.csv(here("NAICS/naics_codes.csv")) %>% 
  select(c(2,3))

colnames(naics_codes) <- c("industry_code", "industry_desc")
```

```{r, include = FALSE}
naics_2 <- naics_codes %>% 
  filter(str_length(industry_code) == 2 | industry_code == "31-33") %>% 
  mutate(industry_code = case_when(
    industry_code == "31-33" ~ 31.33, 
    TRUE ~ as.numeric(industry_code)
  ))
```

```{r}
naics_sub <- function(var, num){
   as.numeric(str_sub({{ var }}, 1, num))
}
```

```{r}
library(tidycensus)
 us_pop <- get_estimates(geography = "county", product = "population", vintage = 2019)
```

#### Helper Functions

```{r}
normalize <- function(data, var){
  
  data %>% 
    ungroup() %>% 
    mutate(var_mean = mean({{ var }}, na.rm = TRUE), 
           var_sd = sd({{ var }}, na.rm = TRUE), 
           norm_var = ({{ var }} - var_mean) / var_sd) %>% 
    select(-c(var_mean, var_sd))
  
  }
```


```{r}
gr_normalize <- function(data, var){
  
  data %>% 
    mutate(var_mean = mean({{ var }}, na.rm = TRUE), 
           var_sd = sd({{ var }}, na.rm = TRUE), 
           norm_var = case_when(
             !is.na(var_sd) ~ (({{ var }} - var_mean) / var_sd), 
           is.na(var_sd) ~ (({{ var }} - var_mean) / 1)))
  
  }
```

```{r}
mn_normalize <- function(data, var){
  
  data %>% 
    mutate(var_mean = mean({{ var }}, na.rm = TRUE), 
           norm_var = ({{ var }} / var_mean))
  
  }
```

```{r}
mn_normalize1 <- function(data, var){
  
  data %>% 
    mutate(var_mean = median({{ var }}, na.rm = TRUE), 
           norm_var = ({{ var }} / var_mean))
  
  }
```


```{r}
rob_norm <- function(data, var){
  
  data %>% 
    ungroup() %>% 
    mutate(var_mean = median({{ var }}, na.rm = TRUE), 
           var_sd = mad({{ var }}, na.rm = TRUE), 
           norm_var = ({{ var }} - var_mean) / var_sd) %>% 
    select(-c(var_mean, var_sd))
  
  }
```

```{r}
med_norm <- function(data, var){
  
  data %>% 
    ungroup() %>% 
    filter()
    mutate(var_med = median({{ var }}, na.rm = TRUE), 
           var_sd = sd({{ var }}, na.rm = TRUE), 
           norm_var = ({{ var }} - var_med) / var_sd) %>% 
    select(-c(var_med, var_sd))
  
  }
```


```{r}
summ_create <- function(data, var){
  data %>% 
    reframe(mean_var = mean({{ var }}, na.rm = TRUE), 
            sd_var = sd({{ var }}, na.rm = TRUE), 
            min_var = min({{ var }}, na.rm = TRUE), 
            max_var = max({{ var }}, na.rm = TRUE)) %>% 
    mutate(across(.cols = everything(), ~round(., 2)))
}
```

# Introduction 

This document generates graphs and models to measure heterogeneity in agglomeration across different dimensions.


# Data Prep

Industry Crosswalk Completeness


```{r}
naics_count <- naics_codes %>% mutate(naics_digits = str_length(industry_code)) %>% filter(naics_digits == 6) %>% mutate(naics_code = as.numeric(industry_code)) %>% filter(naics_code >= 300000 & naics_code < 400000) %>% mutate(naics_3 = naics_sub(naics_code, 3)) %>% left_join(ind_crosswalk %>% select(naics_3 = naics_3digit, naics_3digit_label) %>% distinct()) %>% group_by(naics_3digit_label) %>% count()
```


```{r}
ind_count <- ind_crosswalk %>% group_by(naics_3digit_label) %>% count() %>% rename(ind_c = n)
```

```{r}
naics_count %>% left_join(ind_count) %>% ggplot() + geom_col(aes(x = n, y = reorder(naics_3digit_label, n))) + geom_col(aes(x = ind_c, y = reorder(naics_3digit_label, n)), fill = "lightblue")
```

```{r}
 naics_count %>% left_join(ind_count) %>% ungroup() %>%   mutate(ind_share = ind_c/n, mean_ind = mean(ind_share)) %>% ggplot() + geom_point(aes(x = ind_share, y = reorder(naics_3digit_label, ind_share))) + geom_vline(aes(xintercept = mean_ind))

```


```{r}
manf_supply <- supply_table_final %>% 
  filter(naics_3digit >= 300 & naics_3digit < 400) %>% 
  left_join(sup_com_agg) %>% 
  mutate(manf_percent = value_num / total_commodity_output) %>% #percentage of a given output that is manufactured by a given manufacturing industry
  left_join(ind_agg) %>% 
  mutate(supply_percent = value_num / industry_output)   #percentage of total industry supply that a given output makes up
```

# Results 

We start by importing our data with our measures of agglomeration. 

## Load Data

### Agglomeration Data

```{r}
final_cbp_results <- readRDS(here("Final Data/final_cbp_io_centers_0526.RDS"))
```


```{r}
state_quads <- readRDS(here("State Data/state_quadrants_1.RDS"))
```


```{r}
final_results_merge <- final_cbp_results %>% 
  filter(!is.na(state_abbr)) %>% 
  left_join(ind_crosswalk %>% rename(ind_code = industry_code)) %>% 
  left_join(state_quads %>% select(state_abbr, state_quadrant))
  # mutate(horz_emp = output_emp * (total_inds / (total_inds - output_zeros)),
  #         vert_emp = supply_emp * (total_inds / (total_inds - supply_zeros))) %>% 
  # mutate(across(.cols = c(horz_emp, vert_emp), ~ case_when(
  #   total_inds - supply_zeros == 0 ~ 0, 
  #   TRUE ~ .
  # ))) %>% 
  # select(horz_emp, vert_emp, everything())
```

### R&D Data

```{r}
rd_output <- manf_supply %>% 
  filter(commodity_code == "541700") %>% 
  select(ind_code = industry_code, rd_com_perc = manf_percent, rd_sup_perc = supply_percent, rd_output = value_num) %>% 
  mutate(rd_manf = rd_output / sum(rd_output)) %>% 
  left_join(ind_crosswalk %>% rename(ind_code = industry_code), .) %>% 
  mutate(across(.cols = c(rd_com_perc, rd_sup_perc, rd_manf), ~case_when(
    is.na(.) ~ 0, 
    TRUE ~ .
  ))) %>% 
  mutate(rd_manf_wins = Winsorize(rd_manf, prob = c(0,.99)), 
         rd_sup_wins = Winsorize(rd_sup_perc, prob = c(0,.99)), 
         rd_com_wins = Winsorize(rd_com_perc, prob = c(0,.99)))
  # mutate(rd_com_log = case_when(
  #   rd_com_perc > 0 ~ log(rd_com_perc)), 
  #   rd_sup_log = case_when(rd_sup_perc > 0 ~ log(rd_sup_perc))) %>% 
  # normalize(rd_com_log) %>% 
  # rename(rd_com_z = norm_var) %>% 
  # normalize(rd_sup_log) %>% 
  # rename(rd_sup_z = norm_var)
```

### Materials Intensity

```{r}
#Take the aggregate industry output measures and summarize them. 
manf_ind <- ind_agg %>% 
  mutate(naics_3digit = as.numeric(str_sub(industry_code, 1, 3))) %>% 
  left_join(ind_3digit) %>% 
  filter(naics_3digit >= 300 & naics_3digit < 400) %>% 
  #FIX MISSING VALUES WITH 0
  mutate(across(.cols = c(3:7), ~ case_when(
    is.na(.) ~ 0, 
    TRUE ~ .)),
    val_ratio = value_added/industry_output, 
    input_ratio = intermediary_inputs/industry_output, 
    import_ratio = imports/intermediary_inputs) 
```

```{r}
manf_inputs <- use_table_final %>% 
  filter(naics_3digit >= 300 & naics_3digit < 400) %>% 
  select(-c(value, value_clean)) %>% 
  left_join(manf_ind) %>% 
  mutate(input_share = value_num / intermediary_inputs) %>% 
  ungroup() %>% 
  arrange(industry_code) %>% 
  mutate(com_code_3 = as.numeric(str_sub(commodity_code, 1, 3)))
```

```{r}
mat_intensity <- manf_inputs %>% 
  group_by(industry_code) %>% 
  mutate(mats_manf = case_when(
    com_code_3 < 400 ~ value_num), 
         manf_only = case_when(
           com_code_3 >= 300 & com_code_3 < 400 ~ value_num), 
         mats_manf_dist = case_when(
           com_code_3 < 500 ~ value_num)) %>% 
  mutate(across(.cols = c(mats_manf, manf_only, mats_manf_dist), ~ sum(., na.rm = TRUE))) %>% 
  mutate(across(.cols = c(mats_manf, manf_only, mats_manf_dist), ~ ./intermediary_inputs)) %>% 
  select(ind_code = industry_code, industry_desc, mats_manf, manf_only, mats_manf_dist, intermediary_inputs, naics_3digit_label)  %>% 
  distinct() 
  # normalize(manf_only) %>% rename(manf_z = norm_var) %>% select(-c(var_mean, var_sd))
  
```

### R&D X MATS

```{r}
rd_mats <- rd_output %>% 
  left_join(mat_intensity) %>% 
  normalize(manf_only) %>%
  rename(manf_z = norm_var) %>% 
  normalize(rd_manf_wins) %>% 
  rename(rd_z = norm_var) %>% 
  normalize(rd_sup_perc) %>% 
  rename(rd_sup_z = norm_var) %>% 
  mutate(rd_quads = case_when(
    rd_z >= 0 & manf_z >= 0 ~ "High R&D and Manufacturing Intensity",
    rd_z < 0 & manf_z >= 0 ~ "High Manufacturing Intensity, Low R&D Intensity",
    rd_z < 0 & manf_z < 0 ~ "Low Manufacturing and R&D Intensity",
    rd_z >= 0 & manf_z < 0 ~ "High R&D Intensity, Low Manufacturing Intensity",
    is.na(rd_z) ~ "High Manufacturing Intensity, Low R&D Intensity"
  ))
```

```{r}
rd_sup <- rd_mats %>% 
  filter(rd_sup_perc > 0) %>% 
  ggplot(aes(text = paste(industry_desc, ind_code, sep =", "))) + 
  geom_point(aes(x = log(rd_sup_perc), y = manf_only, fill = naics_3digit_label), shape = 21, size = 4) + 
  guides(fill = "none") + 
  scale_fill_manual(values = emp_ind_vector) + 
  labs(x = "Log R&D Share of Total Value of Industry Outputs", y = "Manufactured Share of Industry Intermediate Inputs") + 
  theme_bw() + 
  axis_theme
```

```{r}
rd_com <-  rd_mats %>% 
  ggplot(aes(text = paste(industry_desc, ind_code, sep =", "))) + 
  geom_point(aes(x = log(rd_com_perc), y = manf_only, fill = naics_3digit_label), shape = 21, size = 4) + 
  guides(fill = "none") + 
  scale_fill_manual(values = emp_ind_vector) + 
  theme_bw() 
```

```{r}
corners <- c("Custom.roll.forming", "Metal can & box & light guage manufacturing", "Aircraft.manufacturing", "Automobile.manufacturing", "Soybean.and.other.oilseed.processing", "Seafood.product.preparation.and.packaging", "Secondary.smelting.and.alloying.of.aluminum", "Pharmaceutical.preparation.manufacturing", "Electronic.computer.manufacturing", "Semiconductor.and.related.device.manufacturing")
```

#### Figure 4

```{r}
rd_corners <- rd_mats %>% 
  filter(rd_manf > 0 ) %>% 
  mutate(industry_desc = case_when(str_detect(industry_desc, "Metal.can") ~ "Metal can & box & light guage manufacturing", TRUE ~ industry_desc)) %>% 
  mutate(ind_lab = case_when(industry_desc %in% corners ~ industry_desc)) %>% 
  mutate(rd_manf = log(rd_manf))

#FIGURE 4
manf_rd <- rd_corners %>% 
  ggplot(aes(text = paste(industry_desc, ind_code, sep =", "))) + 
    geom_point(aes(x = rd_manf, y = manf_only, fill = naics_3digit_label), color = "Dark Grey", shape = 21, size = 4, alpha = 0.9) + 
  geom_point(data = rd_corners %>% filter(!is.na(ind_lab)), aes(x = rd_manf, y = manf_only, fill = naics_3digit_label), color = "black", shape = 21, size = 5) + 
  guides(fill = "none", color = "none") + 
  scale_fill_manual(values = emp_ind_vector) + 
  scale_color_manual(values = emp_ind_vector) + 
  labs(x = "Log Industry Share of Total Value of Manufacturing Sector R&D", y = "Manufactured Share of the Value of Intermediate Inputs") + 
  theme_bw() + 
  axis_theme
```

# The Distribution of Measures

The variables in our dataset are rather dramatically skewed. 

```{r}
final_results_merge %>% 
  mutate(output_emp = output_emp*100) %>% 
  summ_create(output_emp)
```


```{r}
hist(final_results_merge$output_emp)
```

```{r}
final_results_merge %>% 
  summ_create(supply_emp)
```

```{r}
hist(final_results_merge$supply_emp)
```


As such, to account for this skew in the underlying data, we explore a few different options. We consider 1) winsorizing the data; 2) splitting the data into two samples (one for large population centers and one for the rest of the sample); and 3) centering our data around county-mean values. 

## Winsorization

In this approach, we replace extreme values of our data with less extreme values. 


```{r}
final_wins <- final_results_merge %>% 
  mutate(horz_win = Winsorize(output_emp*100, prob = c(0,.99)),
         vert_win = Winsorize(supply_emp*100, prob = c(0,.99))) %>% 
  select(horz_win, output_emp, vert_win, supply_emp, everything())
```


```{r}
final_wins %>% 
  normalize(horz_win) %>% 
  summ_create(norm_var)
```
```{r}
hist(final_wins$horz_win)
```

### Correlations

```{r}
ind_dets <- ind_agg %>% left_join(ind_crosswalk, .) %>% 
  filter(!is.na(intermediary_inputs), !is.na(industry_output)) %>% 
  mutate(imports = case_when(
    is.na(imports) ~ 0, 
    TRUE ~ imports
  )) %>% 
  mutate(imp_share = imports/intermediary_inputs) %>% 
  mutate(across(.cols = c(imp_share, value_added), ~ Winsorize(.,  prob = c(0,.99), na.rm = TRUE))) %>% 
  normalize(imp_share) %>% 
  rename(imp_z = norm_var) %>% 
  normalize(value_added) %>% 
  rename(value_z = norm_var, ind_code = industry_code) %>% select(-c(industry_desc))
```


```{r}
final_data_wins <- final_wins %>% 
  left_join(rd_mats) %>% 
  normalize(horz_win) %>% 
  rename(horz_z = norm_var) %>% 
  normalize(vert_win) %>% 
  rename(vert_z = norm_var) %>% 
  mutate(ind_wins = Winsorize(ind_tot_emp_nat, prob = c(0,.99)), 
         county_wins = Winsorize(county_lq_emp, prob = c(0,.99))) %>% 
  normalize(ind_wins) %>% 
  rename(ind_z = norm_var) %>% 
  normalize(county_wins) %>% 
  rename(county_z = norm_var) %>% 
  left_join(ind_dets)
```

```{r}
horz_lm_wins <- lm(horz_z ~ ind_z + county_z + rd_z + manf_z + vert_z - 1, data = final_data_wins)
```

```{r}
vert_lm_wins <- lm(vert_z ~ ind_z + county_z + rd_z + manf_z + horz_z - 1, data = final_data_wins)
```

```{r}
export_summs(horz_lm_wins, vert_lm_wins, digits = 3)
```

```{r}
horz_lm_wins_2 <- lm(horz_z ~ ind_z + county_z + rd_z + manf_z + vert_z + imp_z + value_z - 1, data = final_data_wins)
```

```{r}
vert_lm_wins_2 <- lm(vert_z ~ ind_z + county_z + rd_z + manf_z + horz_z  + imp_z + value_z  - 1, data = final_data_wins)
```

```{r}
export_summs(horz_lm_wins_2, vert_lm_wins_2, digits = 3)
```

#### County Fixed Effects

```{r}
library(plm)
```

```{r}
horz_fe <- plm(horz_z ~ ind_z + rd_z + manf_z + vert_z, data = final_data_wins, 
               index = c("NAME", "ind_code"), model = "within")
```

```{r}
vert_fe <- plm(vert_z ~ ind_z + rd_z + manf_z + horz_z, data = final_data_wins, 
               index = c("NAME", "ind_code"), model = "within")
```

```{r}
export_summs(horz_fe, vert_fe)
```

## County Normalization 

### Full Sample 

```{r}
final_results_county <- final_results_merge %>% 
  left_join(rd_mats) %>% 
  group_by(NAME) %>% 
  gr_normalize(output_emp) %>% 
  rename(horz_z = norm_var) %>% 
  gr_normalize(supply_emp) %>% 
  rename(vert_z = norm_var) %>% 
  select(horz_z, vert_z, everything()) 
  # ungroup() %>% SOME OBSERVATIONS ARE MISSING BECAUSE THEY ARE THE ONLY INDUSTRY IN A GIVEN COUNTY, and AS SUCH HAVE 0 SD
  # group_by(state_abbr) %>% 
  # gr_normalize(output_emp) %>% 
  # rename(horz_state = norm_var) %>% 
  # gr_normalize(supply_emp) %>% 
  # rename(vert_state = norm_var) %>% 
  # mutate(horz_z = case_when(
  #   is.na(horz_z) ~ horz_state, 
  #   TRUE ~ horz_z ), 
  #   vert_z = case_when(
  #     is.na(vert_z) ~ vert_state, 
  #     TRUE ~ vert_z
  #   ))
```

### County Averages

```{r}
county_agg <- final_results_merge %>% 
  group_by(NAME) %>% 
  reframe(horz_mean = mean(output_emp), vert_mean = mean(supply_emp)) %>% 
  mutate(across(.cols = c(horz_mean, vert_mean), ~ case_when(. > 0 ~ log(.)))) %>% 
  normalize(horz_mean) %>% 
  rename(horz_c_z = norm_var) %>% 
  normalize(vert_mean) %>% 
  rename(vert_c_z = norm_var) 
```


```{r}
county_graph <- final_results_merge %>% 
  filter(supply_emp > 0) %>% 
  group_by(NAME) %>% 
  reframe(horz_mean = mean(output_emp), vert_mean = mean(supply_emp)) %>% 
  mutate(across(.cols = c(horz_mean, vert_mean), ~ log(.))) %>% 
  normalize(horz_mean) %>% 
  rename(horz_c_z = norm_var) %>% 
  normalize(vert_mean) %>% 
  rename(vert_c_z = norm_var) %>% 
  ggplot(aes(text = NAME)) + 
  geom_point(aes(x = horz_c_z, y = vert_c_z)) + 
  geom_vline(xintercept = 0) + 
  geom_hline(yintercept = 0) + 
  geom_abline(slope = 1, intercept = 0)
```


```{r}
distance_from_origin <- function(x, y) {
  # Calculate squared distance to avoid square root in loop (faster)
  squared_distance <- (x^2) + (y^2)
  # Return the square root of the squared distance (actual distance)
  sqrt(squared_distance)
}
```


```{r}
county_quad <- county_agg %>% 
  mutate(agg_quad = case_when(
    horz_c_z >= 0 & vert_c_z >= 0 ~ "High Agglomeration", 
    horz_c_z < 0 & vert_c_z >= 0 ~ "Supplier Agglomeration", 
    horz_c_z >=0 & vert_c_z < 0 ~ "Peer Agglomeration", 
    horz_c_z < 0 & vert_c_z < 0 ~ "Low Agglomeration"
  ),
  agg_dist = distance_from_origin(horz_c_z, vert_c_z)) %>% 
  mutate(agg_quad = case_when(
    is.na(agg_quad) & horz_c_z >=0 ~ "Peer Agglomeration", 
    is.na(agg_quad) & horz_c_z < 0 ~ "Low Agglomeration", 
    TRUE ~ agg_quad
  )) %>% 
  mutate(agg_large = case_when(agg_quad == "Low Agglomeration" ~ agg_quad, TRUE ~ "High Agglomeration"),
         agg_label = case_when(
    agg_quad == "High Agglomeration" ~ "High Agglomeration Counties", 
   agg_quad == "Supplier Agglomeration" ~ "High Vertical, Low Horizontal Agglomeration Counties", 
    agg_quad == "Peer Agglomeration" ~ "High Horizontal, Low Vertical Agglomeration Counties", 
   agg_quad == "Low Agglomeration" ~ "Low Agglomeration Counties"
  ))
```


### County Quads to Sample 

```{r}
final_quads <- final_results_county %>% 
  left_join(county_quad %>% 
              select(agg_quad, agg_large, agg_label, NAME, horz_c_z, vert_c_z)) %>% 
  select(agg_quad, agg_large, horz_c_z, vert_c_z, everything())
```

```{r}
quad_cols <- c("#438cc3", "#53FF33", "#E7298A", "#E6AB02")
```

```{r}
full_sample_blank <- final_results_county %>%
  ggplot(aes(text = paste(NAME, industry_desc, sep = ", "))) + 
  geom_point(aes(x = horz_z, y = vert_z, fill = naics_3digit_label), shape = 21, size = 3, alpha = 0) + 
    scale_fill_manual(values = emp_ind_vector)+ 
    guides(fill = "none") + 
  geom_abline(slope = 1, intercept = 0) + 
  # geom_vline(xintercept = 0, linetype = 2) + 
  # geom_hline(yintercept = 0, linetype = 2) + 
  # geom_abline(slope = 1, intercept = 1, linetype = 2) + geom_abline(slope = 1, intercept = -1, linetype = 2) +
  labs(x = "Horizontal (Peer) Agglomeration \nEmployment, County X Industry", y = "Vertical (Supply-Chain) Agglomeration \nEmployment, County X Industry") + 
  theme_bw() + 
  axis_theme
```

```{r}
#LQ Tests

horz_lq <- final_quads %>%
    ggplot(aes(text = paste(NAME, industry_desc, sep = ", "))) + 
    geom_point(aes(x = log(ind_emp_lq), y = horz_z, fill = naics_3digit_label), shape = 21, size = 3, alpha = 0.9) + 
    scale_fill_manual(values = emp_ind_vector)+ guides(fill = "none") + theme_bw()
```

```{r}
vert_lq <- final_quads %>%
    ggplot(aes(text = paste(NAME, industry_desc, sep = ", "))) + 
    geom_point(aes(x = log(ind_emp_lq), y = vert_z, fill = naics_3digit_label), shape = 21, size = 3, alpha = 0.9) + 
    scale_fill_manual(values = emp_ind_vector)+ guides(fill = "none") + theme_bw()
```



```{r}
full_sample <- final_results_county %>%
  ggplot(aes(text = paste(NAME, industry_desc, sep = ", "))) + 
  geom_point(aes(x = horz_z, y = vert_z, fill = naics_3digit_label), shape = 21, size = 3, alpha = 0.9) + 
    scale_fill_manual(values = emp_ind_vector)+ 
    guides(fill = "none") + 
  geom_abline(slope = 1, intercept = 0) + 
  geom_vline(xintercept = 0, linetype = 2) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_abline(slope = 1, intercept = 1, linetype = 2) + geom_abline(slope = 1, intercept = -1, linetype = 2) +
  labs(x = "Horizontal (Peer) Agglomeration \nEmployment, County X Industry", y = "Vertical (Supply-Chain) Agglomeration \nEmployment, County X Industry") + 
  theme_bw() + 
  axis_theme
```

```{r}
full_sample + facet_wrap(~factor(rd_quads, levels = c("High Manufacturing Intensity, Low R&D Intensity", "High R&D and Manufacturing Intensity", "Low Manufacturing and R&D Intensity", "High R&D Intensity, Low Manufacturing Intensity")))
```


## Focus Industries

```{r}
detailed_ind_list <- c("334413", "311910", "335911", "336411")
```


```{r}
quad_inds <- final_results_county %>% 
  filter(ind_code %in% detailed_ind_list) 

quad_ind_cols <- get_col_match(quad_inds) 

focus_ind_counties <- quad_inds %>%
  ggplot(aes(text = NAME)) + 
  geom_point(aes(x = log(output_emp), log(supply_emp), fill = naics_3digit_label), shape = 21, size = 5) + 
  # geom_point(aes(x = horz_mean, y = vert_mean), fill = "grey", shape = 21, size = 5) + 
  scale_fill_manual(values = quad_ind_cols) + 
  guides(fill = "none", size = "none") +
  # geom_vline(xintercept = 0, linetype = 2) + 
  # geom_hline(yintercept = 0, linetype = 2) + 
  # geom_abline(slope = 1, intercept = 0) + 
  theme_bw() + 
  labs(x = "Horizontal (Peer) Agglomeration \nEmployment, County X Industry", y = "Vertical (Supply-Chain) Agglomeration \nEmployment, County X Industry")  + 
  facet_wrap(~factor(industry_desc, levels = c("Storage.battery.manufacturing", "Aircraft.manufacturing", "Snack.food.manufacturing", "Semiconductor.and.related.device.manufacturing"))) + 
  axis_theme + 
  theme(strip.text = element_text(size = 16))
```

### Corner Industries  

```{r}
rd_mats_val <- rd_mats %>% left_join(ind_dets) %>% ggplot(aes(x = log(value_added), y = log(rd_com_perc), fill = naics_3digit_label, text = industry_desc)) + guides(fill = "none") + scale_fill_manual(values = emp_ind_vector) + geom_point(size = 5, shape = 21) + facet_wrap(~factor(rd_quads, levels = c("High Manufacturing Intensity, Low R&D Intensity", "High R&D and Manufacturing Intensity", "Low Manufacturing and R&D Intensity", "High R&D Intensity, Low Manufacturing Intensity"))) + labs(x = "Log Industry Value Addded", y = "Log Industry Share of Manufacturing R&D") + theme_bw() + axis_theme
```


```{r}
corner_vals <- c("Industrial.process.furnace.and.oven.manufacturing", "Petrochemical.manufacturing", "Plastics.material.and.resin.manufacturing", "Totalizing.fluid.meter.and.counting.device.manufacturing", "Aircraft.manufacturing", "Pharmaceutical.preparation.manufacturing","Secondary.smelting.and.alloying.of.aluminum", "Photographic.and.photocopying.equipment.manufacturing", "Petroleum.refineries", "Dental.laboratories", "Electronic.computer.manufacturing", "Semiconductor.and.related.device.manufacturing")
```



```{r}
corners <- c("Custom.roll.forming", "Metal can & box & light guage manufacturing", "Aircraft.manufacturing", "Automobile.manufacturing", "Pharmaceutical.preparation.manufacturing", "Secondary.smelting.and.alloying.of.aluminum", "Soybean.and.other.oilseed.processing",  "Seafood.product.preparation.and.packaging", "Electronic.computer.manufacturing")
```


```{r}
corner_inds <- final_results_county %>% 
  mutate(industry_desc = case_when(
    str_detect(industry_desc, "Metal.can..box") ~ "Metal can & box & light guage manufacturing", 
    TRUE ~ industry_desc
  )) %>% 
  filter(industry_desc %in% corners) %>% 
  select(ind_code, industry_desc, naics_3digit_label) %>% 
  distinct()

corner_cols <- get_col_match(corner_inds)
```

```{r}
corner_graph <- final_results_county %>%
  mutate(industry_desc = case_when(
    str_detect(industry_desc, "Metal.can..box") ~ "Metal can & box & light guage manufacturing", 
    TRUE ~ industry_desc
  )) %>% 
  filter(industry_desc %in% corners) %>% 
  # group_by(ind_code) %>% 
  # mutate(horz_mean = mean(horz_z), 
  #        vert_mean = mean(vert_z)) %>% 
  ggplot(aes(text = NAME)) + 
  geom_point(aes(x = horz_z, y = vert_z, fill = naics_3digit_label), shape = 21, size = 3, alpha = 0.9) + 
    scale_fill_manual(values = corner_cols)+ 
    guides(fill = "none") + 
  # geom_point(aes(x = horz_mean, y = vert_mean), fill = "grey", shape = 21, size = 5) + 
  geom_abline(slope = 1, intercept = 0) + 
  facet_wrap(~factor(industry_desc, levels =  corners), ncol = 5, nrow = 2) + 
  geom_vline(xintercept = 0) + 
  geom_hline(yintercept = 0) + 
  # geom_abline(slope = 1, intercept = 1, linetype = 2) + geom_abline(slope = 1, intercept = -1, linetype = 2) + 
   labs(x = "County-Industry Horizontal Agglomeration", y = "County-Industry Vertical Agglomeration") + 
  theme_bw() + 
  theme(axis.text = element_text(size = 10), 
        axis.title = element_text(size = 18), 
         strip.text.x = element_text(size = 10))
```

## Industry Normalization 

### Full Sample 

```{r}
final_results_ind <- final_results_merge %>% 
  left_join(rd_mats) %>% 
  group_by(ind_code) %>% 
  gr_normalize(output_emp) %>% 
  rename(horz_z = norm_var) %>% 
  gr_normalize(supply_emp) %>% 
  rename(vert_z = norm_var) %>% 
  select(horz_z, vert_z, everything()) 
  # ungroup() %>% SOME OBSERVATIONS ARE MISSING BECAUSE THEY ARE THE ONLY INDUSTRY IN A GIVEN COUNTY, and AS SUCH HAVE 0 SD
  # group_by(state_abbr) %>% 
  # gr_normalize(output_emp) %>% 
  # rename(horz_state = norm_var) %>% 
  # gr_normalize(supply_emp) %>% 
  # rename(vert_state = norm_var) %>% 
  # mutate(horz_z = case_when(
  #   is.na(horz_z) ~ horz_state, 
  #   TRUE ~ horz_z ), 
  #   vert_z = case_when(
  #     is.na(vert_z) ~ vert_state, 
  #     TRUE ~ vert_z
  #   ))
```

```{r}
full_sample_blank_ind <- final_results_ind %>%
  ggplot(aes(text = paste(NAME, industry_desc, sep = ", "))) + 
  geom_point(aes(x = horz_z, y = vert_z, fill = naics_3digit_label), shape = 21, size = 3, alpha = 0) + 
    scale_fill_manual(values = emp_ind_vector)+ 
    guides(fill = "none") + 
  geom_abline(slope = 1, intercept = 0) + 
  # geom_vline(xintercept = 0, linetype = 2) + 
  # geom_hline(yintercept = 0, linetype = 2) + 
  # geom_abline(slope = 1, intercept = 1, linetype = 2) + geom_abline(slope = 1, intercept = -1, linetype = 2) +
  labs(x = "Horizontal (Peer) Agglomeration \nEmployment, County X Industry", y = "Vertical (Supply-Chain) Agglomeration \nEmployment, County X Industry") + 
  theme_bw() + 
  axis_theme
```


```{r}
full_sample_ind <- final_results_ind %>%
  ggplot(aes(text = paste(NAME, industry_desc, sep = ", "))) + 
  geom_point(aes(x = horz_z, y = vert_z, fill = naics_3digit_label), shape = 21, size = 3, alpha = 0.9) + 
    scale_fill_manual(values = emp_ind_vector)+ 
    guides(fill = "none") + 
  geom_abline(slope = 1, intercept = 0) + 
  geom_vline(xintercept = 0, linetype = 2) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_abline(slope = 1, intercept = 1, linetype = 2) + geom_abline(slope = 1, intercept = -1, linetype = 2) +
  labs(x = "Horizontal (Peer) Agglomeration \nEmployment, County X Industry", y = "Vertical (Supply-Chain) Agglomeration \nEmployment, County X Industry") + 
  theme_bw() + 
  axis_theme
```

```{r}
full_sample_ind + facet_wrap(~factor(rd_quads, levels = c("High Manufacturing Intensity, Low R&D Intensity", "High R&D and Manufacturing Intensity", "Low Manufacturing and R&D Intensity", "High R&D Intensity, Low Manufacturing Intensity")))
```


### Focus Industries

```{r}
detailed_ind_list <- c("334413", "311910", "335911", "336411")
```


```{r}
quad_counties <- final_results_ind %>% 
  filter(ind_code %in% detailed_ind_list) 

quad_count_cols <- get_col_match(quad_counties) 

focus_counties <- quad_counties %>%
  ggplot(aes(text = NAME)) + 
  geom_point(aes(x = horz_z, vert_z, fill = naics_3digit_label), shape = 21, size = 5) + 
  # geom_point(aes(x = horz_mean, y = vert_mean), fill = "grey", shape = 21, size = 5) + 
  scale_fill_manual(values = quad_count_cols) + 
  guides(fill = "none", size = "none") +
  geom_vline(xintercept = 0, linetype = 2) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_abline(slope = 1, intercept = 0) + 
  theme_bw() + 
  labs(x = "Horizontal (Peer) Agglomeration \nEmployment, County X Industry", y = "Vertical (Supply-Chain) Agglomeration \nEmployment, County X Industry")  + 
  facet_wrap(~factor(industry_desc, levels = c("Storage.battery.manufacturing", "Aircraft.manufacturing", "Snack.food.manufacturing", "Semiconductor.and.related.device.manufacturing"))) + 
  axis_theme + 
  theme(strip.text = element_text(size = 16))
```

### Corner Industries  

```{r}
corners <- c("Millwork", "Custom.roll.forming", "Metal can & box & light guage manufacturing", "Aircraft.manufacturing", "Automobile.manufacturing", "Telephone.apparatus.manufacturing", "Petroleum.refineries", "Soybean.and.other.oilseed.processing", "Secondary.smelting.and.alloying.of.aluminum", "Pharmaceutical.preparation.manufacturing", "Semiconductor.and.related.device.manufacturing", "Electronic.computer.manufacturing")
```


```{r}
corner_counties <- final_results_ind %>% 
  mutate(industry_desc = case_when(
    str_detect(industry_desc, "Metal.can..box") ~ "Metal can & box & light guage manufacturing", 
    TRUE ~ industry_desc
  )) %>% 
  filter(industry_desc %in% corner_vals) %>% 
  select(ind_code, industry_desc, naics_3digit_label) %>% 
  distinct()

corner_cols <- get_col_match(corner_counties)
```

```{r}
corner_graph_counties <- final_results_ind %>%
  mutate(industry_desc = case_when(
    str_detect(industry_desc, "Metal.can..box") ~ "Metal can & box & light guage manufacturing", 
    TRUE ~ industry_desc
  )) %>% 
  filter(industry_desc %in% corner_vals) %>% 
  # group_by(ind_code) %>% 
  # mutate(horz_mean = mean(horz_z), 
  #        vert_mean = mean(vert_z)) %>% 
  ggplot(aes(text = NAME)) + 
  geom_point(aes(x = horz_z, y = vert_z, fill = naics_3digit_label), shape = 21, size = 3, alpha = 0.9) + 
    scale_fill_manual(values = corner_cols)+ 
    guides(fill = "none") + 
  # geom_point(aes(x = horz_mean, y = vert_mean), fill = "grey", shape = 21, size = 5) + 
  geom_abline(slope = 1, intercept = 0) + 
  facet_wrap(~factor(industry_desc, levels =  corner_vals), ncol = 6, nrow = 2) + 
  geom_vline(xintercept = 0) + 
  geom_hline(yintercept = 0) + 
  # geom_abline(slope = 1, intercept = 1, linetype = 2) + geom_abline(slope = 1, intercept = -1, linetype = 2) + 
   labs(x = "Industry Horizontal Agglomeration \nEmployment, County X Industry", y = "Industry Vertical Agglomeration \nEmployment, County X Industry") + 
  theme_bw() + 
  axis_theme
```



#### Figure 2

```{r}
#FIGURE 2
full_sample_quads <- final_quads %>% mutate(agg_quad = paste("County-Level", agg_quad, sep = " ")) %>% 
  ggplot(aes(text = paste(NAME, industry_desc, sep = ", "))) + 
  geom_point(aes(x = horz_z, y = vert_z, fill = naics_3digit_label), shape = 21, size = 3, alpha = 0.9) + 
    scale_fill_manual(values = emp_ind_vector)+ 
  guides(fill = "none") + 
  geom_abline(slope = 1, intercept = 0) + 
  geom_vline(xintercept = 0, linetype = 2) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_abline(slope = 1, intercept = 1, linetype = 2) + geom_abline(slope = 1, intercept = -1, linetype = 2) +
  labs(x = "Horizontal (Peer) Agglomeration \nCounty X Industry", y = "Vertical (Supply-Chain) Agglomeration \nCounty X Industry") + 
  theme_bw() + 
  facet_wrap(~factor(agg_label, levels = c("High Vertical, Low Horizontal Agglomeration Counties", "High Agglomeration Counties", "Low Agglomeration Counties", "High Horizontal, Low Vertical Agglomeration Counties")))  + 
  axis_theme
```

```{r}
pharma <- final_quads %>% 
  filter(ind_code == "325412") %>% 
  mutate(agg_quad = paste("County-Level", agg_quad, sep = " ")) %>% 
    ggplot(aes(text = paste(NAME, industry_desc, sep = ", "))) + 
    geom_point(aes(x = horz_z, y = vert_z, fill = naics_3digit_label), shape = 21, size = 3, alpha = 0.9) + 
    scale_fill_manual(values = emp_ind_vector)+ 
    guides(fill = "none") + 
    geom_abline(slope = 1, intercept = 0) + 
    geom_vline(xintercept = 0, linetype = 2) + 
    geom_hline(yintercept = 0, linetype = 2) + 
    geom_abline(slope = 1, intercept = 1, linetype = 2) + geom_abline(slope = 1, intercept = -1, linetype = 2) +
    labs(x = "Horizontal (Peer) Agglomeration \nCounty X Industry", y = "Vertical (Supply-Chain) Agglomeration \nCounty X Industry") + 
    theme_bw() + 
    facet_wrap(~factor(agg_label, levels = c("High Vertical, Low Horizontal Agglomeration Counties", "High Agglomeration Counties", "Low Agglomeration Counties", "High Horizontal, Low Vertical Agglomeration Counties")))  + 
    axis_theme
```


```{r}
#Appendix Figure 1
full_sample_quads_nofac <- final_quads %>% mutate(agg_quad = paste("County-Level", agg_quad, sep = " ")) %>% 
  ggplot(aes(text = paste(NAME, industry_desc, sep = ", "))) + 
  geom_point(aes(x = horz_z, y = vert_z, fill = naics_3digit_label), shape = 21, size = 3, alpha = 0.9) + 
    scale_fill_manual(values = emp_ind_vector)+ 
  guides(fill = "none") + 
  geom_abline(slope = 1, intercept = 0) + 
  geom_vline(xintercept = 0, linetype = 2) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_abline(slope = 1, intercept = 1, linetype = 2) + geom_abline(slope = 1, intercept = -1, linetype = 2) +
  labs(x = "Horizontal (Peer) Agglomeration \nCounty X Industry", y = "Vertical (Supply-Chain) Agglomeration \nCounty X Industry") + 
  theme_bw() + 
  axis_theme
```



```{r}
final_quads %>%
  select(-c(horz_z, vert_z)) %>% 
  group_by(agg_quad, NAME) %>% 
  gr_normalize(output_emp) %>% 
  rename(horz_z = norm_var) %>% 
  gr_normalize(supply_emp) %>% 
  rename(vert_z = norm_var) %>% 
  ggplot(aes(text = paste(NAME, industry_desc, sep = ", "))) + 
  geom_point(aes(x = horz_z, y = vert_z, fill = naics_3digit_label), shape = 21, size = 3, alpha = 0.9) + 
    scale_fill_manual(values = emp_ind_vector)+ 
  guides(fill = "none") + 
  geom_abline(slope = 1, intercept = 0) + 
  geom_vline(xintercept = 0, linetype = 2) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_abline(slope = 1, intercept = 1, linetype = 2) + geom_abline(slope = 1, intercept = -1, linetype = 2) +
  labs(x = "Horizontal (Peer) Agglomeration \nEmployment, County X Industry", y = "Vertical (Supply-Chain) Agglomeration \nEmployment, County X Industry") + 
  theme_bw() + 
  facet_wrap(~factor(rd_quads, levels = c("High Manufacturing Intensity, Low R&D Intensity", "High R&D and Manufacturing Intensity", "Low Manufacturing and R&D Intensity", "High R&D Intensity, Low Manufacturing Intensity")))  + 
  axis_theme
```


```{r}
final_quads_norm <- final_quads %>% 
  group_by(agg_quad, NAME) %>% 
  gr_normalize(output_emp) %>% 
  rename(horz_z_quad = norm_var) %>% 
  gr_normalize(supply_emp) %>% 
  rename(vert_z_quad = norm_var) 
```


```{r}
#FIGURE 2
agg_all <- final_quads %>%
  filter(!is.na(agg_quad)) %>% 
  ggplot(aes(text = paste(NAME, industry_desc, sep = ", "))) + 
  geom_point(aes(x = horz_z, y = vert_z, fill = naics_3digit_label), shape = 21, size = 3, alpha = 0.9) + 
    scale_fill_manual(values = emp_ind_vector)+ 
    guides(fill = "none") + 
  geom_abline(slope = 1, intercept = 0) + 
  geom_vline(xintercept = 0, linetype = 2) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  # geom_abline(slope = 1, intercept = 1, linetype = 2) + geom_abline(slope = 1, intercept = -1, linetype = 2) +
  labs(x = "Horizontal (Peer) Agglomeration \nEmployment, County X Industry", y = "Vertical (Supply-Chain) Agglomeration \nEmployment, County X Industry") + 
  facet_wrap(~factor(agg_quad, levels = c("Supplier Agglomeration", "General Agglomeration", "Low Agglomeration", "Peer Agglomeration"))) + 
  theme_bw() + 
  axis_theme
```

```{r}
agg_graph <- function(data) {
  
  data_col <- get_col_match(data)

  data %>% 
    ggplot(aes(text = paste(NAME, industry_desc, sep = ", "))) + 
    geom_point(aes(x = horz_z, y = vert_z, fill = naics_3digit_label), shape = 21, size = 3, alpha = 0.9) + 
      scale_fill_manual(values = data_col)+ 
      guides(fill = "none") + 
    geom_abline(slope = 1, intercept = 0) + 
    geom_vline(xintercept = 0, linetype = 2) + 
    geom_hline(yintercept = 0, linetype = 2) + 
    # geom_abline(slope = 1, intercept = 1, linetype = 2) + geom_abline(slope = 1, intercept = -1, linetype = 2) +
    labs(x = "Horizontal (Peer) Agglomeration \nEmployment, County X Industry", y = "Vertical (Supply-Chain) Agglomeration \nEmployment, County X Industry") + 
    theme_bw() + 
    axis_theme
}
```

```{r}
agg1 <- final_quads %>%
  filter(agg_quad == "Supplier Agglomeration") %>% 
  agg_graph() + 
  facet_wrap(~factor(rd_quads, levels = c("High Manufacturing Intensity, Low R&D Intensity", "High R&D and Manufacturing Intensity", "Low Manufacturing and R&D Intensity", "High R&D Intensity, Low Manufacturing Intensity")))
```

```{r}
agg2 <- final_quads %>%
  filter(agg_quad == "General Agglomeration") %>% 
  agg_graph() + 
  facet_wrap(~factor(rd_quads, levels = c("High Manufacturing Intensity, Low R&D Intensity", "High R&D and Manufacturing Intensity", "Low Manufacturing and R&D Intensity", "High R&D Intensity, Low Manufacturing Intensity")))
```

```{r}
agg3 <- final_quads %>%
  filter(agg_quad == "Low Agglomeration") %>% 
  agg_graph() + 
  facet_wrap(~factor(rd_quads, levels = c("High Manufacturing Intensity, Low R&D Intensity", "High R&D and Manufacturing Intensity", "Low Manufacturing and R&D Intensity", "High R&D Intensity, Low Manufacturing Intensity")))
```

```{r}
agg4 <- final_quads %>%
  filter(agg_quad == "Peer Agglomeration") %>% 
  agg_graph() + 
  facet_wrap(~factor(rd_quads, levels = c("High Manufacturing Intensity, Low R&D Intensity", "High R&D and Manufacturing Intensity", "Low Manufacturing and R&D Intensity", "High R&D Intensity, Low Manufacturing Intensity")))
```

```{r}
agg1 <- final_quads %>%
  filter(agg_quad == "Supplier Agglomeration") %>% 
  agg_graph() + 
  facet_wrap(~factor(naics_3digit_label))
```

```{r}
agg2 <- final_quads %>%
  filter(agg_quad == "High Agglomeration") %>% 
  agg_graph() + 
  facet_wrap(~factor(naics_3digit_label))
```

```{r}
agg3 <- final_quads %>%
  filter(agg_quad == "Low Agglomeration") %>% 
  agg_graph() + 
  facet_wrap(~factor(naics_3digit_label))
```

```{r}
agg4 <- final_quads %>%
  filter(agg_quad == "Peer Agglomeration") %>% 
  agg_graph() + 
  facet_wrap(~factor(naics_3digit_label))
```

```{r}
(agg1 + agg2) / (agg3 + agg4)
```

#### Figure 3

```{r}
detailed_ind_list <- c("334413", "311700", "336411")
```

```{r}
quad_inds <- final_quads %>% 
  group_by(agg_label, NAME) %>% 
  gr_normalize(output_emp) %>% 
  rename(horz_z_quad = norm_var) %>% 
  gr_normalize(supply_emp) %>% 
  rename(vert_z_quad = norm_var) %>% 
  filter(ind_code %in% detailed_ind_list) 

quad_ind_cols <- get_col_match(quad_inds) 

quad_ind_counties <- quad_inds %>%
  ggplot(aes(text = NAME)) + 
  geom_point(aes(x = horz_z_quad, vert_z_quad, shape = agg_label, fill = naics_3digit_label, color = naics_3digit_label), size = 5) + 
  # scale_fill_manual(values = c(quad_cols[1], quad_cols[2], quad_cols[4])) +
  # geom_point(aes(x = horz_mean, y = vert_mean), fill = "grey", shape = 21, size = 5) + 
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  # geom_abline(slope = 1, intercept = 0) + 
  scale_shape_manual(values=c(21, 2, 0, 8))+
  scale_fill_manual(values = quad_ind_cols) + 
  scale_color_manual(values = quad_ind_cols) + 
  guides(fill = "none", color = "none") + 
  theme_bw() + 
  labs(x = "Horizontal (Peer) Agglomeration \nEmployment, County X Industry", y = "Vertical (Supply-Chain) Agglomeration \nEmployment, County X Industry", shape = "")  + 
  facet_wrap(~factor(industry_desc, levels = c("Seafood.product.preparation.and.packaging", "Semiconductor.and.related.device.manufacturing", "Aircraft.manufacturing"))) + 
  axis_theme + 
  theme(legend.position = "bottom", legend.text = element_text(size = 13))
```

```{r}
quad_inds <- final_quads %>% 
  group_by(agg_label, NAME) %>% 
  gr_normalize(output_emp) %>% 
  rename(horz_z_quad = norm_var) %>% 
  gr_normalize(supply_emp) %>% 
  rename(vert_z_quad = norm_var) %>% 
  filter(ind_code %in% detailed_ind_list) 

quad_ind_cols <- get_col_match(quad_inds) 

quad_ind_counties <- quad_inds %>%
  ggplot(aes(text = NAME)) + 
  geom_point(aes(x = horz_z_quad, vert_z_quad, fill = naics_3digit_label), shape = 21, size = 5, color = "black") + 
  # scale_fill_manual(values = c(quad_cols[1], quad_cols[2], quad_cols[4])) +
  # geom_point(aes(x = horz_mean, y = vert_mean), fill = "grey", shape = 21, size = 5) + 
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  # geom_abline(slope = 1, intercept = 0) + 
  scale_shape_manual(values=c(21, 2, 0, 8))+
  scale_fill_manual(values = quad_ind_cols) +
  guides(fill = "none") + 
  theme_bw() + 
  labs(x = "Horizontal (Peer) Agglomeration \nCounty X Industry", y = "Vertical (Supply-Chain) Agglomeration \nCounty X Industry", fill = "")  + 
  facet_wrap(~factor(industry_desc, levels = c("Seafood.product.preparation.and.packaging", "Semiconductor.and.related.device.manufacturing", "Aircraft.manufacturing"))) + 
  axis_theme + 
  theme(legend.position = "bottom", legend.text = element_text(size = 16))
```


```{r}
semi_c <- final_results_merge %>% filter(ind_code == "334413") %>% reframe(mean_horz = mean(output_emp), mean_vert = mean(supply_emp))

seafood_c <- final_results_merge %>% filter(ind_code == "311700") %>% reframe(mean_horz = mean(output_emp), mean_vert = mean(supply_emp))

aircraft_c <- final_results_merge %>% filter(ind_code == "336411") %>% reframe(mean_horz = mean(output_emp), mean_vert = mean(supply_emp)).
```


#### MESC Foucs

```{r}
mesc_list <- c("335911", "335912", "336111")
```

```{r}
mesc_inds <- final_quads %>% 
  group_by(agg_label, NAME) %>% 
  gr_normalize(output_emp) %>% 
  rename(horz_z_quad = norm_var) %>% 
  gr_normalize(supply_emp) %>% 
  rename(vert_z_quad = norm_var) %>% 
  filter(ind_code %in% mesc_list) 

mesc_ind_cols <- get_col_match(mesc_inds) 

mesc_counties <- mesc_inds %>%
  ggplot(aes(text = NAME)) + 
  geom_point(aes(x = horz_z_quad, vert_z_quad, fill = state_abbr), shape = 21, size = 5) + 
  # scale_fill_manual(values = c(quad_cols[1], quad_cols[2], quad_cols[4])) +
  # geom_point(aes(x = horz_mean, y = vert_mean), fill = "grey", shape = 21, size = 5) + 
  geom_vline(xintercept = 0, linetype = 2) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_label(aes(x = horz_z_quad, vert_z_quad, fill = state_abbr, label = state_abbr), shape = 21, size = 5)+
  # geom_abline(slope = 1, intercept = 0) + 
  scale_fill_brewer(palette = "Set3") + 
  guides(fill = "none") + 
  theme_bw() + 
  labs(x = "Peer Agglomeration \nEmployment, County X Industry", y = "Supply-Chain Agglomeration \nEmployment, County X Industry", fill = "")  + 
  facet_wrap(~industry_desc) + 
  axis_theme + 
  theme(legend.position = "bottom", legend.text = element_text(size = 16))
```

#### Figure 6 (Panel B)

```{r}
semi_counties <- final_quads %>% 
  filter(ind_code %in% c("334413")) %>% 
  mutate(semi_quad = case_when(
    horz_z >= 0 & vert_z >= 0 ~ "High", 
    horz_z >= 0 & vert_z < 0 ~ "Supplier", 
    horz_z < 0 & vert_z >= 0 ~ "Peer", 
    horz_z < 0 & vert_z < 0 ~ "Low"
  ))
```



```{r}
focus_counties <- c("Maricopa County, Arizona", "Washington County, Oregon", "Dallas County, Texas", "Ada County, Idaho", "Santa Clara County, California")
```


```{r}
other_counties <- c("FL", "CA", "MO", "NC")
```

```{r}
corner_states <- c("MO", "FL", "IL", "ME", "MA", "CA")
```


```{r}
defense_states <- c("MA", "OH", "IN", "GA", "FL", "NM", "AZ", "CA") 
```

```{r}
defense_rd <- c("IN", "OH", "AZ", "UT", "PA", "MA", "GA", "NM", "CA", "MO", "NY", "FL", "MI", "TN")
```

```{r}
semi_graphb <- quad_inds %>% filter(ind_code == "334413") %>%
  ggplot(aes(text = NAME)) + 
  # scale_fill_manual(values = c(quad_cols[1], quad_cols[4], quad_cols[2])) +
  geom_label_repel(data = quad_inds %>% filter(ind_code == "334413", NAME %in% focus_counties), aes(x = horz_z_quad, vert_z_quad, label = NAME), fill = "lightgrey", size = 5) + 
   geom_point(aes(x = horz_z_quad, vert_z_quad, fill = agg_quad), shape = 21, size = 5, alpha  = .8) + 
  geom_point(data = quad_inds %>% filter(ind_code == "334413", NAME %in% focus_counties), aes(x = horz_z_quad, vert_z_quad), fill = "lightgrey", shape = 21, size = 5) + 
    scale_fill_manual(values = c(quad_cols[1], quad_cols[4], quad_cols[2])) +

  # geom_vline(xintercept = semi_counties$semi_horz, color = semi_col) + 
  # geom_hline(yintercept = semi_counties$semi_vert, color = semi_col) + 
  guides(fill = "none") + 
  geom_vline(xintercept = 0) + 
  geom_hline(yintercept = 0) + 
  labs(x = "Horizontal (Peer) Agglomeration \nEmployment, County X Industry", y = "Vertical (Supply-Chain) Agglomeration \nEmployment, County X Industry", shape = "")  + 
  theme_bw() + 
  axis_theme
```

```{r}
defense_semi_b <- quad_inds %>% filter(ind_code == "334413") %>%
  ggplot(aes(text = NAME)) + 
  # scale_fill_manual(values = c(quad_cols[1], quad_cols[4], quad_cols[2])) +
   geom_point(aes(x = horz_z_quad, vert_z_quad), shape = 21, size = 5, fill = "lightgrey") + 
  geom_point(data = quad_inds %>% filter(ind_code == "334413", state_abbr %in% defense_states), aes(x = horz_z_quad, y = vert_z_quad, fill = state_abbr), shape = 21, size = 4) +
  geom_label_repel(data = quad_inds %>% filter(ind_code == "334413", state_abbr %in% defense_states), aes(x = horz_z_quad, y = vert_z_quad, label = state_abbr, fill = state_abbr)) + scale_fill_brewer(palette = "Set2") + 
  # geom_vline(xintercept = semi_counties$semi_horz, color = semi_col) + 
  # geom_hline(yintercept = semi_counties$semi_vert, color = semi_col) + 
  guides(fill = "none") + 
  geom_vline(xintercept = 0) + 
  geom_hline(yintercept = 0) + 
  labs(x = "Horizontal (Peer) Agglomeration \nEmployment, County X Industry", y = "Vertical (Supply-Chain) Agglomeration \nEmployment, County X Industry", shape = "")  + 
  theme_bw() + 
  axis_theme
```


```{r}
semi_graph2 <- quad_inds %>% filter(ind_code == "334413") %>%
  ggplot(aes(text = NAME)) + 
  geom_point(aes(x = horz_z_quad, vert_z_quad), shape = 21, size = 5, fill = "#a8e4a0") + 
  scale_fill_manual(values = c(quad_cols[1], quad_cols[4], quad_cols[2])) +
  geom_label_repel(data = quad_inds %>% filter(ind_code == "334413", NAME %in% focus_counties), aes(x = horz_z_quad, vert_z_quad, label = NAME), fill = "lightgrey", size = 5) + 
  geom_point(data = quad_inds %>% filter(ind_code == "334413", NAME %in% focus_counties), aes(x = horz_z_quad, vert_z_quad), fill = "lightgrey", shape = 21, size = 5) + 
  # geom_vline(xintercept = semi_counties$semi_horz, color = semi_col) + 
  # geom_hline(yintercept = semi_counties$semi_vert, color = semi_col) + 
  guides(fill = "none") + 
  geom_vline(xintercept = 0) + 
  geom_hline(yintercept = 0) + 
  labs(x = "County-Industry Horizontal Agglomeration Z-Score \nCounty-Normalized", y = "County-Industry Vertical Agglomeration Z-Score \nCounty-Normalized") + 
  theme_bw() + 
  axis_theme
```


### Maps

```{r}
quad_ranges <- county_quad %>% group_by(agg_quad) %>% reframe(min_dist = round(min(agg_dist),2), max_dist = round(max(agg_dist), 2))

quad_ranges
```


```{r}
county_agg_map_df <- county_quad %>% 
  left_join(counties %>% mutate(NAME = paste(county_name, state_name, sep = ", ")), .)
```

#### Figure 1

```{r}
all_agg_map <- county_agg_map_df %>% 
  ggplot(aes(long, lat, group = group)) + 
  geom_polygon(data = urbnmapr::states, colour = "black", fill = "White") + 
  geom_polygon(data = county_agg_map_df %>% filter(agg_quad == "High Agglomeration"), fill = "#438cc3", alpha = 0.8,  color = "#438cc3") +
  coord_map(projection = "albers", lat0 = 39, lat1 = 45) + 
  geom_polygon(data = county_agg_map_df %>% filter(agg_quad == "Supplier Agglomeration"), fill = "#53FF33", color = "#53FF33", show.legend = FALSE, alpha = 0.8) +
  geom_polygon(data = county_agg_map_df %>% filter(agg_quad == "Peer Agglomeration"), fill = "#E7298A",  color = "#E7298A", show.legend = FALSE, alpha  = 0.8) +
  geom_polygon(data = county_agg_map_df %>% filter(agg_quad == "Low Agglomeration"), fill = "#E6AB02",  color = "#E6AB02", show.legend = FALSE, alpha = 0.6) +
  theme_map() 
  
```

```{r}
all_agg_map_blue <- county_agg_map_df %>% 
  ggplot(aes(long, lat, group = group)) + 
  geom_polygon(data = urbnmapr::states, colour = "black", fill = "White") + 
  geom_polygon(data = county_agg_map_df %>% filter(agg_quad == "General Agglomeration"), fill = "#438cc3", alpha = 0.8,  color = "#438cc3") +
  coord_map(projection = "albers", lat0 = 39, lat1 = 45) +
  theme_map() 
  
```

```{r}
all_agg_map_orange <- county_agg_map_df %>% 
  ggplot(aes(long, lat, group = group)) + 
  geom_polygon(data = urbnmapr::states, colour = "black", fill = "White") + 
  geom_polygon(data = county_agg_map_df %>% filter(agg_quad == "General Agglomeration"), fill = "#438cc3", alpha = 0.8,  color = "#438cc3") +
  coord_map(projection = "albers", lat0 = 39, lat1 = 45) +
  geom_polygon(data = county_agg_map_df %>% filter(agg_quad == "Low Agglomeration"), fill = "#E6AB02",  color = "#E6AB02", show.legend = FALSE, alpha = 0.6) +
  theme_map() 
```

```{r}
all_agg_map_alt <- county_agg_map_df %>% 
  ggplot(aes(long, lat, group = group)) + 
  geom_polygon(data = urbnmapr::states, colour = "black", fill = "White") + 
  geom_polygon(data = county_agg_map_df %>% filter(agg_quad == "General Agglomeration"), fill = "#AA4A44", alpha = 0.8,  color = "#AA4A44") +
  coord_map(projection = "albers", lat0 = 39, lat1 = 45) + 
  geom_polygon(data = county_agg_map_df %>% filter(agg_quad == "Supplier Agglomeration"), fill = "#8DC8AA", color = "#8DC8AA", show.legend = FALSE, alpha = 0.8) +
  geom_polygon(data = county_agg_map_df %>% filter(agg_quad == "Peer Agglomeration"), fill = "#FBCEB1",  color = "#FBCEB1", show.legend = FALSE, alpha  = 0.8) +
  geom_polygon(data = county_agg_map_df %>% filter(agg_quad == "Low Agglomeration"), fill = "#664228",  color = "#664228", show.legend = FALSE, alpha = 0.6) +
  theme_map() 
  
```
  

```{r}

ind_map <- function(data, industry) {
  
  map_df <- final_results_merge %>% 
    select(-c(state_fips, county_fips)) %>% 
    filter(ind_code %in% industry)  %>% left_join(county_agg_map_df)
  

  df_map <- map_df %>% 
    ggplot(aes(long, lat, group = group)) + 
    geom_polygon(data = urbnmapr::states, colour = "black", fill = "white") + 
    geom_polygon(data = map_df %>% filter(agg_quad == "General Agglomeration"), fill = "#438cc3", alpha = 0.8,  color = "#438cc3") +
    coord_map(projection = "albers", lat0 = 39, lat1 = 45) + 
    geom_polygon(data = map_df %>% filter(agg_quad == "Supplier Agglomeration"), fill = "#4ff9c4", color = "#4ff9c4", show.legend = FALSE, alpha = 0.8) +
    geom_polygon(data = map_df %>% filter(agg_quad == "Peer Agglomeration"), fill = "#E7298A",  color = "#E7298A", show.legend = FALSE, alpha  = 0.8) +
    geom_polygon(data = map_df %>% filter(agg_quad == "Low Agglomeration"), fill = "#E6AB02",  color = "#E6AB02", show.legend = FALSE, alpha = 0.8) +
    theme_map() 
  
  return(df_map)
  
}
```

```{r}
#Semiconductor map
county_agg_map_df %>% 
  ind_map("334413")
```

```{r}
county_agg_map_df %>% 
  ind_map(mesc_list[3]) 
```

```{r}
county_agg_map_df %>% 
  ind_map(bat_list)
```


```{r}
all_agg_map <- county_agg_map_df %>% 
  ggplot(aes(long, lat, group = group)) + 
  geom_polygon(data = urbnmapr::states, colour = "black", fill = "black") + 
  geom_polygon(data = county_agg_map_df %>% filter(agg_quad == "General Agglomeration"), aes(fill = agg_dist),  color = "#438cc3", show.legend = FALSE) +
  coord_map(projection = "albers", lat0 = 39, lat1 = 45) + 
  scale_fill_gradient(low = "#f6f1eb", high = "#438cc3", limits =  c(0.00, 4.5)) + 
  new_scale_fill() + 
  geom_polygon(data = county_agg_map_df %>% filter(agg_quad == "Supplier Agglomeration"), aes(fill = agg_dist), color = "#4ff9c4", show.legend = FALSE) +
  scale_fill_gradient(low = "#f6f1eb", high = "#4ff9c4", limits =  c(0, 2.5)) + 
  new_scale_fill() + 
  geom_polygon(data = county_agg_map_df %>% filter(agg_quad == "Peer Agglomeration"), aes(fill = agg_dist),  color = "#E7298A", show.legend = FALSE) +
  scale_fill_gradient(low = "#f6f1eb", high = "#E7298A", limits =  c(0, 4.5)) + 
  new_scale_fill() + 
  geom_polygon(data = county_agg_map_df %>% filter(agg_quad == "Low Agglomeration"), aes(fill = agg_dist),  color = "#E6AB02", show.legend = FALSE) +
  scale_fill_gradient(low = "#f6f1eb", high = "#E6AB02", limits =  c(0, 6.2)) +  
  theme_map() 
  
```

```{r}
bat_list <- mesc_list[-3]
```


```{r}
county_agg_map_df %>% 
  ggplot(aes(long, lat, group = group)) + 
  geom_polygon(data = urbnmapr::states, colour = "black", fill = "black") + 
  geom_polygon(data = county_agg_map_df %>% filter(agg_quad == "General Agglomeration"), aes(fill = agg_dist),  color = "#438cc3", show.legend = FALSE) +
  coord_map(projection = "albers", lat0 = 39, lat1 = 45) + 
  scale_fill_gradient(low = "#f6f1eb", high = "#438cc3", limits =  c(0.00, 4.5)) + 
  new_scale_fill() + 
  geom_polygon(data = county_agg_map_df %>% filter(agg_quad == "Supplier Agglomeration"), aes(fill = agg_dist), color = "#4ff9c4", show.legend = FALSE) +
  scale_fill_gradient(low = "#f6f1eb", high = "#4ff9c4", limits =  c(0, 2.5)) + 
  new_scale_fill() + 
  geom_polygon(data = county_agg_map_df %>% filter(agg_quad == "Peer Agglomeration"), aes(fill = agg_dist),  color = "#E7298A", show.legend = FALSE) +
  scale_fill_gradient(low = "#f6f1eb", high = "#E7298A", limits =  c(0, 4.5)) + 
  new_scale_fill() + 
  geom_polygon(data = county_agg_map_df %>% filter(agg_quad == "Low Agglomeration"), aes(fill = agg_dist),  color = "#E6AB02", show.legend = FALSE) +
  scale_fill_gradient(low = "#f6f1eb", high = "#E6AB02", limits =  c(0, 6.2)) +  
  geom_polygon(data = county_agg_map_df %>% filter(ind_code %in% bat_list),  color = "Black", show.legend = FALSE) +
  theme_map() 
```


#### MESC Focus


```{r}
county_agg_map_df %>% 
  filter(ind_code %in% mesc_list) %>% 
  ggplot(aes(long, lat, group = group)) + 
  geom_polygon(data = urbnmapr::states, colour = "black", fill = "White") + 
  geom_polygon(aes(fill = agg_quad)) +
  theme_map() 
```

#### Semiconductor Industry

```{r}
semi_inds <- c("334413")
```

```{r}
"#438cc3" "#53FF33" "#E7298A" "#E6AB02"
```


```{r}
semi_graph <- final_quads %>% filter(ind_code %in% semi_inds) %>%  mutate(agg_quad = paste("County-Level", agg_quad, sep = " ")) %>% 
    ggplot(aes(text = paste(NAME, industry_desc, sep = ", "))) + 
    geom_point(aes(x = horz_z, y = vert_z, fill = agg_quad), shape = 21, size = 3, alpha = 0.9) + 
    guides(fill = "none") +
  scale_fill_manual(values = c("#438cc3", "#E6AB02", "#53FF33")) + 
    geom_abline(slope = 1, intercept = 0) + 
    geom_vline(xintercept = 0, linetype = 2) + 
    geom_hline(yintercept = 0, linetype = 2) + 
    geom_abline(slope = 1, intercept = 1, linetype = 2) + geom_abline(slope = 1, intercept = -1, linetype = 2) +
    labs(x = "Horizontal (Peer) Agglomeration \nCounty X Industry", y = "Vertical (Supply-Chain) Agglomeration \nCounty X Industry") + 
    theme_bw() + 
    facet_wrap(~factor(industry_desc, levels = c("Semiconductor.and.related.device.manufacturing", "Printed.circuit.assembly..electronic.assembly..manufacturing", "Other.electronic.component.manufacturing", "Semiconductor.machinery.manufacturing")))  + 
    axis_theme
```

```{r}
semi_graph + geom_label(aes(x = horz_z, y = vert_z, fill = agg_quad, label = state_abbr), shape = 21, size = 3, alpha = 0.9) 
```


```{r}
semi_counties_all <- final_results_merge %>% 
  filter(ind_code %in% semi_inds) %>% 
  select(NAME, ind_code, industry_desc, ind_emp_lq) %>% 
  distinct()
```


```{r}
semi_map <- function(data, industry){
  
  data %>% 
    filter(ind_code == industry) %>% 
    left_join(county_agg_map_df) %>% 
    ggplot(aes(long, lat, group = group)) + 
  geom_polygon(data = urbnmapr::states, colour = "black", fill = "White") + 
  geom_polygon(aes(fill = ind_emp_lq, color = ind_emp_lq)) +
    scale_fill_distiller(palette = "Spectral") + 
    scale_color_distiller(palette = "Spectral") + 
    guides(fill = "none") + 
  theme_map() 
  
}
```

```{r}
get_name <- function(industry){
  
  ind_crosswalk %>% 
    filter(industry_code %in% industry) %>% 
    select(industry_desc) %>% 
    unlist() %>% 
    unname() 
  
}
```


```{r}
semi_1 <- semi_map(semi_counties_all, semi_inds[1]) + labs(title = get_name(semi_inds[1]))
semi_2 <- semi_map(semi_counties_all, semi_inds[2]) + labs(title = get_name(semi_inds[2]))
semi_3 <- semi_map(semi_counties_all, semi_inds[3]) + labs(title = get_name(semi_inds[3]))
semi_4 <- semi_map(semi_counties_all, semi_inds[4]) + labs(title = get_name(semi_inds[4]))
```

```{r}
(semi_1 + semi_2) / (semi_3 + semi_4)
```


```{r}
county_agg_map_df %>% 
  filter(ind_code %in% semi_inds) %>% 
  ggplot(aes(long, lat, group = group)) + 
  geom_polygon(data = urbnmapr::states, colour = "black", fill = "White") + 
  geom_polygon(aes(fill = agg_quad)) +
  theme_map() 
```

### Quad Correlations

```{r}
final_data_test <- final_results_merge %>% left_join(county_quad %>% select(NAME, agg_quad)) %>% group_by(agg_quad) %>% left_join(rd_mats) %>% 
    gr_normalize(output_emp) %>% 
    rename(horz_z = norm_var) %>% 
    gr_normalize(supply_emp) %>% 
    rename(vert_z = norm_var) %>% 
    gr_normalize(ind_tot_emp_nat) %>% rename(ind_z = norm_var) %>% gr_normalize(county_lq_emp) %>% rename(county_z = norm_var) %>% gr_normalize(rd_manf) %>% rename(rd_z1 = norm_var)
```


```{r}
horz_1 <- lm(horz_z ~ ind_z + county_z + rd_z + manf_z + vert_z - 1, data = final_data_test %>% filter(agg_quad == "General Agglomeration"))
horz_2 <- lm(horz_z ~ ind_z + county_z + rd_z + manf_z + vert_z - 1, data = final_data_test %>% filter(agg_quad == "Supplier Agglomeration"))
horz_3 <- lm(horz_z ~ ind_z + county_z + rd_z + manf_z + vert_z - 1, data = final_data_test %>% filter(agg_quad == "Low Agglomeration"))
horz_4 <- lm(horz_z ~ ind_z + county_z + rd_z + manf_z + vert_z - 1, data = final_data_test %>% filter(agg_quad == "Peer Agglomeration"))
```

```{r}
vert_1 <- lm(vert_z ~ ind_z + county_z + rd_z + manf_z + horz_z - 1, data = final_data_test %>% filter(agg_quad == "General Agglomeration"))
vert_2 <- lm(vert_z ~ ind_z + county_z + rd_z + manf_z + horz_z - 1, data = final_data_test %>% filter(agg_quad == "Supplier Agglomeration"))
vert_3 <- lm(vert_z ~ ind_z + county_z + rd_z + manf_z + horz_z - 1, data = final_data_test %>% filter(agg_quad == "Low Agglomeration"))
vert_4 <- lm(vert_z ~ ind_z + county_z + rd_z + manf_z + horz_z - 1, data = final_data_test %>% filter(agg_quad == "Peer Agglomeration"))
```


```{r}
export_summs(horz_1, horz_3, horz_2, horz_4)
```

```{r}
export_summs(vert_1, vert_3, vert_2, vert_4)
```


# MAP QUADS to GRANULARITY EXPANSION


# LOG TESTS


```{r}
final_results_logs <- final_results_merge %>%
  filter(supply_emp > 0) %>% 
  left_join(rd_mats) %>% 
  # mutate(output_emp = output_emp * (total_inds / (total_inds - output_zeros)),
  #        supply_emp = supply_emp * (total_inds / (total_inds - supply_zeros))) %>%
  # mutate(output_emp = output_emp / (county_tot_emp/sum(county_tot_emp)),
  #        supply_emp = supply_emp / (county_tot_emp/sum(county_tot_emp))) %>%
  mutate(across(.cols = c(output_emp, supply_emp), ~log(.))) %>% 
  normalize(output_emp) %>% 
  rename(horz_z = norm_var) %>% 
  normalize(supply_emp) %>% 
  rename(vert_z = norm_var) %>% 
  select(output_emp, supply_emp, horz_z, vert_z, everything()) %>% 
  mutate(rd_com_log = case_when(rd_com_perc > 0 ~ log(rd_com_perc))) %>% 
  normalize(rd_com_log) %>% 
  rename(rd_log_z = norm_var)
  # normalize(log_horz) %>% 
  # rename(horz_z = norm_var) %>% 
  # normalize(log_vert) %>% 
  # rename(vert_z = norm_var) 

```

### Figure 6 (Panel A)

```{r}
quad_logs
```


```{r}
semi_graph <- final_results_logs %>% filter(ind_code == "334413") %>% left_join(county_quad %>% select(NAME, agg_quad)) %>% 
  ggplot(aes(text = NAME)) + 
  geom_point(aes(x = horz_z, vert_z, fill = agg_quad), shape = 21, size = 5) + 
  scale_fill_manual(values = c(quad_cols[1], quad_cols[4], quad_cols[2])) +
  geom_label_repel(data = final_results_logs %>% filter(ind_code == "334413", NAME %in% focus_counties), aes(x = horz_z, vert_z, label = NAME), fill = "lightgrey", size = 5) + 
  geom_point(data = final_results_logs %>% filter(ind_code == "334413", NAME %in% focus_counties), aes(x = horz_z, vert_z), fill = "lightgrey", shape = 21, size = 5) + 
  # geom_vline(xintercept = semi_counties$semi_horz, color = semi_col) + 
  # geom_hline(yintercept = semi_counties$semi_vert, color = semi_col) + 
  geom_vline(xintercept = 0) + 
  geom_hline(yintercept = 0) + 
  xlim(-3,4) + 
  ylim(-2, 2) + 
  labs(x = "County-Industry Horizontal Agglomeration Z-Score \nLog-Normalized", y = "County-Industry Vertical Agglomeration Z-Score \nLog-Normalized") + 
  theme_bw() + 
  guides(fill = "none") + 
  axis_theme
```

```{r}
defense_semis <- semi_graph + geom_label_repel(data = final_results_logs %>% filter(ind_code == "334413", state_abbr %in% defense_states), aes(x = horz_z, y = vert_z, label = state_abbr, fill = state_abbr)) + scale_fill_brewer(palette = "Dark2")
```



### Log Correlations

```{r}
final_data_all <- final_results_logs %>% 
  mutate(log_ind = log(ind_tot_emp_nat), 
         log_county = log(county_lq_emp)) %>% 
  normalize(log_ind) %>% 
  rename(ind_z = norm_var) %>% 
  normalize(log_county) %>% 
  rename(county_z = log_county) %>% left_join(county_quad %>% select(NAME, agg_quad))
```


```{r}
horz_lm_full <- lm(horz_z ~ ind_z + county_z + rd_log_z + manf_z + vert_z, data = final_data_all)
```

```{r}
vert_lm_full <- lm(vert_z ~ ind_z + county_z + rd_log_z + manf_z + horz_z, data = final_data_all)
```

```{r}
export_summs(horz_lm_full, vert_lm_full)
```

```{r}
horz_lm_full_2 <- lm(horz_z ~ ind_z + county_z + rd_log_z + manf_z + vert_z + imp_z + val_z - 1, data = final_data_vals)
```

```{r}
vert_lm_full_2 <- lm(vert_z ~ ind_z + county_z + rd_log_z + manf_z + horz_z + imp_z + val_z - 1, data = final_data_vals)
```

```{r}
export_summs(horz_lm_full_2, vert_lm_full_2)
```


```{r}
horz_1 <- lm(horz_z ~ ind_z + county_z + rd_z + manf_z + vert_z - 1, data = final_data_all %>% filter(agg_quad == "General Agglomeration"))
horz_2 <- lm(horz_z ~ ind_z + county_z + rd_z + manf_z + vert_z - 1, data = final_data_all %>% filter(agg_quad == "Supplier Agglomeration"))
horz_3 <- lm(horz_z ~ ind_z + county_z + rd_z + manf_z + vert_z - 1, data = final_data_all %>% filter(agg_quad == "Low Agglomeration"))
horz_4 <- lm(horz_z ~ ind_z + county_z + rd_z + manf_z + vert_z - 1, data = final_data_all %>% filter(agg_quad == "Peer Agglomeration"))
```

```{r}
vert_1 <- lm(vert_z ~ ind_z + county_z + rd_z + manf_z + horz_z - 1, data = final_data_all %>% filter(agg_quad == "General Agglomeration"))
vert_2 <- lm(vert_z ~ ind_z + county_z + rd_z + manf_z + horz_z - 1, data = final_data_all %>% filter(agg_quad == "Supplier Agglomeration"))
vert_3 <- lm(vert_z ~ ind_z + county_z + rd_z + manf_z + horz_z - 1, data = final_data_all %>% filter(agg_quad == "Low Agglomeration"))
vert_4 <- lm(vert_z ~ ind_z + county_z + rd_z + manf_z + horz_z - 1, data = final_data_all %>% filter(agg_quad == "Peer Agglomeration"))
```


```{r}
export_summs(horz_1, horz_3, horz_2, horz_4)
```

# Split Samples

We now split the samples into large population areas, and other counties. 

```{r}
final_split <- final_results_merge %>% 
  mutate(large_center = case_when(
    county_tot_emp > 500000 ~ "Large", 
    county_tot_emp < 500000 ~ "Small"
  )) %>% 
  group_by(large_center) %>% 
  gr_normalize(output_emp) %>% 
  rename(horz_z = norm_var) %>% 
  gr_normalize(supply_emp) %>% 
  rename(vert_z = norm_var) 
```

```{r}
split_graph <- final_split %>%
  ggplot(aes(text = paste(NAME, industry_desc, sep = ", "))) + 
  geom_point(aes(x = horz_z, y = vert_z, fill = naics_3digit_label), shape = 21, size = 3, alpha = 0.9) + 
    scale_fill_manual(values = emp_ind_vector)+ 
    guides(fill = "none") + 
  geom_abline(slope = 1, intercept = 0) + 
  geom_vline(xintercept = 0, linetype = 2) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_abline(slope = 1, intercept = 1, linetype = 2) + geom_abline(slope = 1, intercept = -1, linetype = 2) +
  labs(x = "Horizontal (Peer) Agglomeration \nEmployment, County X Industry", y = "Vertical (Supply-Chain) Agglomeration \nEmployment, County X Industry") + 
  theme_bw() + 
  facet_wrap(~large_center) +
  axis_theme 
```



```{r}
large_counties <- final_results_merge %>% 
  filter(county_tot_emp > 500000)
```

```{r}
smaller_co
```

