---
title: "Mapping Manufacturing Activity"
author: "Nikhil Kalathil"
date: '2023-06-26'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this document, we will use previously cleaned data to map manufacturing activity. 

We start by loading our packages and datasets.

```{r, include = FALSE}
library(tigris)
library(tidyverse)
library(here)
library(leaflet)
library(ggrepel)
library(RColorBrewer)

title_theme <- theme(axis.text = element_text(size = 14), 
        axis.title = element_text(size = 18), 
        title = element_text(size = 20))

axis_theme <- theme(axis.text = element_text(size = 10), 
        axis.title = element_text(size = 18))
```

```{r, include = FALSE}
area_codes <- readRDS(here("State Data/area_crosswalk.RDS")) %>% 
  mutate(area_title = str_remove(area_title, " -- Statewide")) %>% 
  mutate(area_fips = case_when(
    nchar(area_fips) == 4 ~ paste("0", area_fips, sep = ""), 
    TRUE ~ area_fips
  ))
```


```{r, include = FALSE}
states <- data.frame(state_abbr = state.abb, area_title = state.name)
```

```{r, include = FALSE}
area_codes <- left_join(area_codes, states)
```

The three datasets we load are a state/national level dataset on state 2-digit manufacturing employment and GDP, benchmarked against national averages; a dataset on 2-digit county manufacturing employment; and a dataset on state level 3-digit manufacturing GDP. We also load a dataset of national trends to benchmark against. 

```{r}
manf_data <- readRDS(here("State Data/manf_clean.RDS"))
county_emp <- readRDS(here("State Data/county_employment.RDS"))
state_ind <- readRDS(here("State Data/state_ind.RDS"))
nat_gdp <- readRDS(here("State Data/national_gdp.RDS"))
```

# Base maps

We then use the urbnmapr package to get our baseline maps for plotting. We get a state map: 

```{r, include = FALSE}
states_sf <- states(cb = TRUE, resolution = "20m") %>%
shift_geometry(position = "outside")

states_leaflet <- states_sf %>% 
  sf::st_transform('+proj=longlat +datum=WGS84')
```

```{r}
states_sf %>% 
  ggplot(aes()) +
  geom_sf(fill = "grey", color = "#ffffff")
```

We can also make an interactive map

```{r}
m <- leaflet(states_leaflet) 
m %>% 
  addPolygons(color = "black")
```

As well as a county map: 

```{r, include = FALSE}
county_sf <- counties(cb = TRUE)

county_leaflet <- county_sf %>% 
  sf::st_transform('+proj=longlat +datum=WGS84')
```

We can then easily join our existing datasets for some easy mapping. We start with our state level maps to begin with. 

# State level maps

In general, we are looking to create a series of maps. The first map shows raw levels, the second map benchmarks these levels against national or state averages, the third map shows change between two specific years (either in percent change or raw percentage points in the case of manufacturing share), and the fourth map benchmarks this change against national or state averages. 

As we work towards these maps, we will endeavor to explore data interactively to better contextualize our information. The high degree of heteregeneity across states, counties, and manufacturing industries suggests that at the moment, manufacturing ecosystems could be considered "high-dimensional" data structures. In our work, we seek to simplify the number of dimensions that we need to evaluate manufacturing ecosytems across, and create meanigful categorizations of state manufacturinge ecosystems. 

```{r}
state_manf <- states_leaflet %>% 
  left_join(manf_data %>% rename(NAME = area_title))
```


```{r}
state_manf_2019 <- state_manf %>% 
  filter(year == 2019, !is.na(NAME))
```

## 2019 Employment Levels

```{r}
state_manf_emp_1 <- ggplot() +
  geom_sf(state_manf %>% filter(year == 2019),
          mapping = aes(fill = emp/1000, geometry = geometry), 
          color = "black", size = 0.25) +
  labs(fill = "Manufacturing Employment, 2019 \n (Thousands)") + 
  scale_fill_distiller(palette = "BuPu") + 
  theme_void()
```

```{r}
state_manf_emp_1
```

While we can see some clear trends, this static image is perhaps not the best way to process our data. Instead, we can endeavor to build an interactive map that provides us with the information that we care about.

To accomplish this, we have to create a color mapping function, plot a base map using leaflet (addPolygons function), and then add highlight options that contain customized, dynamic text to populate the labels with (highlightOptions). This work uses the leaflet package. 


```{r}
state_manf_2019 <- state_manf_2019 %>% 
  mutate(emp_k = emp / 1000,
    emp_thousands = prettyNum(emp, big.mark = ',',scientific=FALSE))
```

As we go through setting up our first interactive map, we will try and define some functions to help us create new maps later. 

```{r}

emp_col <- colorNumeric(palette = "BuPu", domain = state_manf_2019$emp_k, reverse = TRUE)
```

```{r}
#DEFINE COLOR FUNCTION
col_def <- function(data, var, col_scale){ 
  
  col_pal <- colorNumeric(palette = col_scale, domain = data$var, reverse = TRUE)
  
  }
```

```{r}
emp_col <- col_def(state_manf_2019, emp_k, "BuPu")
```


```{r}
#Create Labels for popups
labels <- sprintf(
  "<strong>%s</strong><br/>%s <br/> <i>Avg Monthly Employees <br/> %g, (NAICS 31-33)</i>",
  state_manf_2019$NAME, state_manf_2019$emp_thousands, state_manf_2019$year
) %>% lapply(htmltools::HTML)
```


```{r}
#Define dynamic column selector function 

var_def <- function(data, var) {
  
  var_list <- data %>% 
    tibble() %>% 
    select({{ var }}) %>% 
    unlist()
  
  names(var_list) <- NULL 
  
  return(var_list)
}
```


```{r}
#Define dynamic label Creator

label_1 <- function(data, var, text, sector){
  
  name_vec <- var_def(data, NAME) 
  
  year_vec <- var_def(data, year)
  
  val_vec <- var_def(data, {{ var }})
  
  if(typeof(year_vec) == "character"){
    
    sprintf(paste("<strong>%s</strong><br/>%s <br/> <i>", text, "<br/> %s,", sector, "</i>", sep = ""),
  name_vec, val_vec, year_vec
  
    ) %>% lapply(htmltools::HTML) }
  
  else{
  
  sprintf(paste("<strong>%s</strong><br/>%s <br/> <i>", text, "<br/> %g,", sector, "</i>", sep = ""),
  name_vec, val_vec, year_vec
  
) %>% lapply(htmltools::HTML) } 
  
}
```

```{r}
emp_labels <- label_1(state_manf_2019, emp_thousands, "Avg Monthly Employees", "(NAICS 31-33)")
```

```{r}
# Build map (Add Pologyons)
m <-  state_manf_2019 %>% 
  leaflet() %>% 
  addPolygons(
  fillColor = ~emp_col(state_manf_2019$emp_k),
  weight = 2,
  opacity = 1,
  color = "black",
  dashArray = "3",
  fillOpacity = 0.7, 
  highlightOptions = highlightOptions(
    weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 0.7,
    bringToFront = TRUE),
  label = emp_labels,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto"))
  
```


We can then add a legend to this map 

```{r}
emp_map_1 <- m %>% 
  addLegend(pal = emp_col, values = ~emp_k, opacity = 0.7, title = "2019 Monthly NAICS 31-33 <br/> Employment",
  position = "bottomleft")

emp_map_1
```


We now pause to define some more generic functions for mapping. 


```{r}
build_map <- function(data, var1, label_var, colors, text, sector, legend_title) { 
  
  col_list <- var_def(data, {{ var1 }})
  
  col_fun <- col_def(data, var1, colors)
  
  popup_lablels <- label_1(data, {{ label_var }}, text, sector)
  
  m <- data %>% 
  leaflet() %>% 
  addPolygons(
  fillColor = ~col_fun(col_list),
  weight = 2,
  opacity = 1,
  color = "black",
  dashArray = "3",
  fillOpacity = 0.7, 
  highlightOptions = highlightOptions(
    weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 0.7,
    bringToFront = TRUE),
  label = popup_lablels,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto")) %>% 
    addLegend(pal = col_fun, values = col_list, opacity = 0.7, title = legend_title,
  position = "bottomleft")
  
  return(m)
  }
```

We see that we can use this function to build maps quickly! 

```{r}
build_map(state_manf_2019, emp, emp_thousands, "BuPu", "Avg Monthly Emploment", " (NAICS 31-33)", "2019 NAICS 31-33 <br/> Monthly Employees")
```

## 2019 GDP Levels

Now, we turn to GDP. 

```{r}
state_manf_gdp_1 <- ggplot() +
  geom_sf(state_manf %>% filter(year == 2019),
          mapping = aes(fill = gdp_manf/10000, geometry = geometry ), 
          color = "black", size = 0.25) +
  labs(fill = "Annual GDP from NAICS 31-33\n Billions of 2012 $") + 
  scale_fill_distiller(palette = "BuPu") + 
  theme_void() 

state_manf_gdp_1
```

```{r}
state_manf_gdp_1 + guides(fill = "none")
```

We can then also make an interactive map, similar to as we did above. First, we just have to clean up variables that we want to display, and then use our previously defined function!

```{r}
state_gdp_2019 <- state_manf_2019 %>% 
  filter(!is.na(gdp_manf)) %>% 
  mutate(gdp_manf_b = gdp_manf/10000,
    gdp_manf_b_clean = round(gdp_manf_b, 2), 
    manf_gdp_share_perc = manf_gdp_share*100, 
    manf_gdp_share_clean = paste(round(manf_gdp_share_perc, 2), "&#37", sep = ""),
    manf_emp_share_perc = manf_emp_share*100, 
    manf_emp_share_clean = paste(round(manf_emp_share_perc, 2), "&#37", sep = ""))
```

```{r}
gdp_manf_1 <- build_map(state_gdp_2019, gdp_manf_b, gdp_manf_b_clean, "BuPu", "Avg Annual GDP, 2012$B", " (NAICS 31-33)", "2019 NAICS 31-33 <br/> Avg Annual GDP (2012$B)")

gdp_manf_1
```
Quickly, we can also plot the correlation between manufacturing employment and manufacturing gdp. 

```{r}
gdp_emp_2019 <- state_manf_2019 %>% 
  ggplot() + 
  geom_point(shape = 21, aes(x = gdp_manf, y = emp), fill = brewer.pal(9, "Set3")[1], color = "black", size = 4, alpha = 0.7) + 
  scale_x_continuous(labels = scales::unit_format(unit = "$B", scale = 1e-4)) + 
  scale_y_continuous(labels = scales::unit_format(unit = "K", scale = 1e-3)) + 
  labs(x = "NAICS 31-33 Annual GDP in Billions of $2012", y = "NAICS 31-33 Average Monthly Employees, Thousands") + 
  theme_bw()

gdp_emp_2019 + geom_text_repel(aes(x = gdp_manf, y = emp, label = STUSPS), max.overlaps = 30) 
```

## 2019 Manufacturing Share

We now turn to manufacturing share of the economy, beginning with GDP: 

### 2019 Manufacturing Share (GDP)

```{r}
gdp_manf_share <- build_map(state_gdp_2019, manf_gdp_share_perc, manf_gdp_share_clean, "BuPu", "Annual &#37 of State GDP", " (NAICS 31-33)", "2019 NAICS 31-33 <br/> Annual &#37 of State GDP")

gdp_manf_share
```
### 2019 Manufacturing Share (Employment)

And also for employment. 

```{r}
emp_manf_share <- build_map(state_gdp_2019, manf_emp_share_perc, manf_emp_share_clean, "BuPu", " &#37 of State Employment", " (NAICS 31-33)", "2019 NAICS 31-33 <br/>  &#37 of State Employment")

emp_manf_share
```

# Trends

From here, we've established basic levels in 2019 for the manufacturing state of the economy, and can now explore how the manufacturing economy in each state has grown between 2010 and 2019. 

To accomplish this, we will bring back some functions we defined in previous work. 

```{r}
manf_state_calc <- function(data, min_year, max_year, sel_vars, mut_vars){ 
  
  data %>% 
    filter(year == min_year | year == max_year)%>%
    arrange(NAME, year) %>% 
    mutate(across(.cols = {{ mut_vars }}, ~ (as.numeric(.x)/lag(as.numeric(.x)) - 1 ))) %>% 
    filter(year == max_year) %>% 
    select( {{ sel_vars }} )

}
```



```{r}
change_calc_emp <- function(data, min_year, max_year){ 
  data %>% 
  filter(year == min_year | year == max_year, !is.na(state_abbr)) %>% 
  arrange(state_abbr, year) %>% 
  mutate(manf_2010 = if_else(
           year == max_year,
           lag(manf_emp_share), 
           NA_real_
         ), 
         emp_share_change = if_else(
           year == max_year,
           manf_emp_share - manf_2010, 
           NA_real_
         ), 
         manf_change = emp_share_change > 0) %>% 
  filter(year == max_year) 
  }
```


```{r}
change_calc_gdp <- function(data, min_year, max_year){ 
  data %>% 
  filter(year == min_year | year == max_year, !is.na(state_abbr)) %>% 
  arrange(state_abbr, year) %>% 
  mutate(manf_2010 = if_else(
           year == max_year,
           lag(manf_gdp_share), 
           NA_real_
         ), 
         gdp_share_change = if_else(
           year == max_year,
           manf_gdp_share - manf_2010, 
           NA_real_
         ), 
         manf_change = gdp_share_change > 0) %>% 
  filter(year == max_year) 
  }
```


We start by examining the percent change in the size of the manufacturing economy between 2010 and 2019. 

```{r}
trends_data_2010_2019 <- state_manf %>%
  filter(!is.na(gdp_manf), !is.na(emp)) %>% 
                manf_state_calc(2010,
                               2019, 
                               c(emp, gdp_manf, state_gdp, tot_emp, NAME),
                               c(emp, gdp_manf, state_gdp, tot_emp)) %>%
  mutate(gdp_manf_perc = gdp_manf*100, 
         emp_perc = emp*100, 
         state_gdp_perc = state_gdp*100, 
         tot_emp_perc = state_gdp*100, 
         gdp_manf_perc_clean = paste(round(gdp_manf_perc, 2), "&#37", sep = ""),
         emp_perc_clean = paste(round(emp_perc, 2), "&#37", sep = ""), 
         state_gdp_perc_clean = paste(round(emp_perc, 2), "&#37", sep = ""), 
         tot_emp_perc_clean = paste(round(emp_perc, 2), "&#37"), 
         year = "2010-2019")
 
```

## 2010-2019 GDP % Change

```{r}
gdp_change_2010_2019 <- build_map(trends_data_2010_2019, gdp_manf_perc, gdp_manf_perc_clean, "YlOrRd", " &#37 Change in Annual GDP", " (NAICS 31-33)", "2019 NAICS 31-33 <br/>  &#37  Change in Annual GDP, <br/> 2010-2019")

gdp_change_2010_2019
```

## 2010-2019 Emp % Change

```{r}
emp_change_2010_2019 <- build_map(trends_data_2010_2019, emp_perc, emp_perc_clean, "YlOrRd", " &#37 Change in Avg Monthly Employment", " (NAICS 31-33)", "2019 NAICS 31-33 <br/>  &#37  Change in <br/> Avg Monthly Employment <br/> 2010-2019")

emp_change_2010_2019
```


We can also then examine the corrleation between percentage change in NAICS 31-33 employment and percentage change in GDP. 

```{r}
gdp_emp_trends <- trends_data_2010_2019 %>% 
  rename(area_title = NAME) %>% 
  left_join(area_codes) %>% 
  ggplot() + 
  geom_point(aes(emp_perc, gdp_manf_perc)) + 
  geom_text_repel(aes(emp_perc, gdp_manf_perc, label = state_abbr)) + 
  labs(x = "2010 to 2019 Percent Change in NAICS 31-33 Employment", y = "2010 to 2019 Percent Change in NAICS 31-33 GDP") + 
  theme_bw() + 
  axis_theme

gdp_emp_trends
```


We now want to benchmark changes in the manufacturing sector against changes in the state economy as a whole. At this point we realize that we need to define a new legend. Earlier, we tried to create a way to dynamically define a label by wrapping the build_map() function in a label function, but this effort failed. As such, we will continue to explicitly define the label and rewrite the build_map() function accordingly. 

We begin with a summary graph of the trend we are attempting to show. 

```{r}
manf_col <- brewer.pal(9, "Set3")[5]
total_col <- "#A5764D"
```

```{r}
trends_map_2010_2019 <- trends_data_2010_2019 %>% 
    rename(area_title = NAME, state_gdp_change = state_gdp) %>% 
    left_join(area_codes) %>% 
    group_by(area_title) %>% 
    left_join(state_manf %>%
                  tibble() %>% 
                  filter(year == 2019) %>% 
                  select(state_abbr, state_gdp)) %>% 
  mutate(manf_sign = gdp_manf_perc > state_gdp_perc, 
         manf_state_dif = state_gdp_perc - gdp_manf_perc) 
```

## 2010-2019 Manufacturing GDP % Change v. State GDP % Change

```{r}
state_change <- trends_map_2010_2019 %>% 
  ggplot() + 
   geom_segment(aes(x = reorder(state_abbr, state_gdp), y = gdp_manf_perc, xend = reorder(state_abbr, state_gdp), yend = state_gdp_perc, color = manf_sign), size = 2) +
  geom_point(aes(x = reorder(state_abbr, state_gdp), y = gdp_manf_perc), size = 4, shape = 21, color = "black", fill = manf_col) + 
  geom_point(aes(x = reorder(state_abbr, state_gdp), y = state_gdp_perc), size = 3, shape = 21, color = "black", fill = total_col) + 
  geom_hline(yintercept = 0, color = "black") + 
  guides(fill = "none", color = "none") + 
  scale_color_manual(values = c(total_col, manf_col))+
  labs(x = "", y = "Percent Change in GDP, 2010 - 2019") + 
  coord_flip() + 
  theme_bw() + 
  axis_theme

state_change
```


We can also view this data differently. 

```{r}
state_manf_gdp <- trends_map_2010_2019 %>% 
  ggplot() + 
  geom_hline(yintercept = 0)+ 
  geom_vline(xintercept = 0) + 
  geom_point(aes(state_gdp_perc, gdp_manf_perc, size = state_gdp, fill = manf_state_dif), shape = 21, color = "black") + 
  scale_fill_gradient(low = total_col, high = manf_col) + 
  geom_text_repel(aes(state_gdp_perc, gdp_manf_perc, label = state_abbr)) +
  guides(fill = "none", size = "none") + 
  theme_bw() + 
  labs(x = "% Change in Annual GDP, 2010-2019 \n All Industries", y = "% Change in Annual GDP, 2010-2019 \n NAICS 31-33")

state_manf_gdp
  
```

To refelect this in leaflet, we need to create one variable that can capture our desired information, and map it to a color. 

```{r}
state_benchmark_col <- colorNumeric(palette ="YlOrBr", domain = trends_map_2010_2019$manf_state_dif)
```

```{r}
nat_sum <- nat_gdp %>% 
  filter(year == 2010 | year == 2019) %>% 
  select(year, gdp_manf, state_gdp) %>% 
  mutate(across(.cols = c(gdp_manf, state_gdp), ~ (as.numeric(.x)/lag(as.numeric(.x)) - 1 ))) %>% 
  filter(year == 2019) %>%
  mutate(manf_state_dif = state_gdp - gdp_manf, 
         nat_manf_clean = paste(round(manf_state_dif*100, 2), "&#37"))
```


```{r}
label_popup <- sprintf(
  "<strong>%s</strong> <br/> 2010 - 2019 <br/> NAICS 31-33  GDP &#37 Change <br/> %s <br/> <i>All Industries GDP &#37 Change <br/> %s </i>",
  trends_map_2010_2019$area_title, trends_map_2010_2019$gdp_manf_perc_clean, trends_map_2010_2019$state_gdp_perc_clean
) %>% lapply(htmltools::HTML)

state_manf_2010_2019 <- trends_map_2010_2019 %>% 
  leaflet() %>% 
  addPolygons(
  fillColor = ~state_benchmark_col(trends_map_2010_2019$manf_state_dif),
  weight = 2,
  opacity = 1,
  color = "black",
  dashArray = "3",
  fillOpacity = 0.7, 
  highlightOptions = highlightOptions(
    weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 0.7,
    bringToFront = TRUE),
  label = label_popup,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto")) %>% 
   addLegend(pal = state_benchmark_col, values = trends_map_2010_2019$manf_state_dif, opacity = 0.7, title = paste("&#37 Point Diff. <br/> (All Industries &#37 Change <br/> - NAICS 31-33 &#37 Change) <br/> National Diff.:", nat_sum$nat_manf_clean[1], sep = ""), 
  position = "bottomleft")
  
```

```{r}
state_manf_2010_2019
```

# 2019 Industry Composition 

We now turn to our industry composition data. Here, we are interested in both understanding which industries are dominant in a state, how these top industries vary across states, and how concentrated the states economy is in a few particular industries. To accomplish this, we will focus on the top 3-5 industries in the state, as well as construct a Herfindahl Hirschman index to measure concentration.

We also read in employment data. 

```{r}
ind_emp_2019 <- readRDS(here("State Data/industry_emp.RDS"))
```

```{r}
industry_titles <- read_csv(here("State Data/industry-titles.csv")) %>% 
  filter(str_length(industry_code) == 3) %>% 
  mutate(industry_code = as.numeric(industry_code))
```



We will perform some of our calculations in our state_ind dataset first, and then merge this dataset with our map. 

```{r}
state_ind_2019 <- state_ind %>% 
  filter(year == 2019) %>% 
  mutate(Description = str_remove(Description, "manufacturing")) %>% 
  group_by(GeoName) %>% 
  arrange(desc(manf_ind_gdp), .by_group = TRUE) %>% 
  mutate(ind_tal = seq(n())) 
```

Exploring this dataset, we see that the dropoff in industry GDP between the "top" industry in a state, and the next highest industry can be quite steep (as in the case of Alaska), or more gradual (as in the case of Alabama)

Interestingly, if we focus on only the top 3 manufacturing industries in a state, we get a list of 12 industries. Expanding this to top 4 gives us a list of 16 industries, 17 for 5, and 18 for 6. 

```{r}
state_ind_2019 %>% 
  filter(ind_tal < 5) %>% 
  ungroup() %>% 
  count(Description)
```


To display our data in a map, we will remember the top line industry, and then create a variable that holds the description of the top 3 along with their industry GDPs. 

```{r}
state_ind_2019_clean <- state_ind_2019 %>% 
  group_by(GeoName) %>% 
  mutate(ind_hhi = sum(ind_share_state**2, na.rm = TRUE)) %>% 
  mutate(gdp_pretty = prettyNum(manf_ind_gdp, big.mark = ',',scientific=FALSE),
    desc_3 = paste(
    Description, ": ", gdp_pretty, "<br/>", 
    lead(Description), ": ", lead(gdp_pretty), "<br/>", 
    lead(Description, 2), ": ", lead(gdp_pretty, 2), sep = ""
  )) %>%
  filter(ind_tal == 1) %>% 
  rename(NAME = GeoName)
```

```{r}
state_ind_2019_map <- left_join(states_leaflet, state_ind_2019_clean) %>% 
  filter(!is.na(ind_hhi))
```

Now, because of differences in what we are trying to display, we will need to use new color and label defining functions to display our map. 

```{r}
#Define Colors
ind_colors <- colorFactor(palette = brewer.pal(12, "Paired"), domain = state_ind_2019_map$Description)
```

```{r}
#Define Labels

ind_labels <- sprintf(
  "<strong>%s</strong> <br/>  HHI: %g <br/> Millions of &#36 2012, Manufacturing Subsector <br/> <i> %s </i>",
  state_ind_2019_map$NAME, state_ind_2019_map$ind_hhi, state_ind_2019_map$desc_3) %>% lapply(htmltools::HTML)
```

Having defined our color scale and labels, we can map our industry data. 

```{r}
state_inds <- state_ind_2019_map %>% 
  leaflet() %>% 
  addPolygons(
  fillColor = ~ind_colors(state_ind_2019_map$Description),
  weight = 2,
  opacity = 1,
  color = "black",
  dashArray = "3",
  fillOpacity = 0.7, 
  highlightOptions = highlightOptions(
    weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 1,
    bringToFront = TRUE),
  label = ind_labels,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto")) %>% 
  addLegend(pal = ind_colors, values = state_ind_2019_map$Description, opacity = 0.7, title = "Highest State 3-Digit <br/>Manufacturing Subsector Annual GDP",
  position = "bottomleft")

state_inds
```

## Employment 

We now look at industry employment by state. 

```{r}
state_ind_2019_emp <- ind_emp_2019 %>% 
  left_join(industry_titles) %>% 
  left_join(manf_data %>% 
              filter(year == 2019) %>% 
              select(area_title, manf_emp = emp, tot_emp)) %>% 
  group_by(area_title) %>% 
  arrange(desc(emp), .by_group = TRUE) %>% 
  mutate(ind_tal_emp = seq(n())) %>% 
  mutate(emp_share = emp/tot_emp,
         pretty_emp = prettyNum(emp, big.mark = ',',scientific=FALSE), 
    ind_hhi_emp = sum(emp_share**2, na.rm = TRUE), 
    Description = str_remove(industry_title, "NAICS"),
    Description = str_remove(Description, "manufacturing"),
    desc_3 = paste(
    Description, ": ", pretty_emp, "<br/>", 
    lead(Description), ": ", lead(pretty_emp), "<br/>", 
    lead(Description, 2), ": ", lead(pretty_emp, 2), sep = ""
  )) 
```

```{r}
state_ind_2019_emp %>% 
  filter(ind_tal_emp < 4) %>% 
  ungroup() %>% 
  count(industry_title)
```

```{r}
ind_emp_cols <- c(brewer.pal(11, "Paired"), brewer.pal(3, "Dark2"))
```

```{r}
state_ind_emp_2019_map <- left_join(states_leaflet, state_ind_2019_emp %>% 
                                   rename(NAME = area_title) %>% 
                                     filter(ind_tal_emp == 1))%>% 
  filter(!is.na(desc_3))
```


```{r}
#Define Colors
ind_colors_emp <- colorFactor(palette = ind_emp_cols, domain = state_ind_emp_2019_map$Description)
```

```{r}
#Define Labels

ind_labels_emp <- sprintf(
  "<strong>%s</strong> <br/>  HHI: %g <br/> Millions of &#36 2012, Manufacturing Subsector <br/> <i> %s </i>",
  state_ind_emp_2019_map$NAME, state_ind_emp_2019_map$ind_hhi_emp, state_ind_emp_2019_map$desc_3) %>% lapply(htmltools::HTML)
```


As above, we prepare a color scheme and popup for our map.

```{r}
state_inds_emp <- state_ind_emp_2019_map %>% 
  leaflet() %>% 
  addPolygons(
  fillColor = ~ind_colors_emp(state_ind_emp_2019_map$Description),
  weight = 2,
  opacity = 1,
  color = "black",
  dashArray = "3",
  fillOpacity = 0.7, 
  highlightOptions = highlightOptions(
    weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 1,
    bringToFront = TRUE),
  label = ind_labels_emp,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto")) 

state_inds_emp %>% 
  addLegend(pal = ind_colors_emp, values = state_ind_emp_2019_map$Description, opacity = 0.7, title = "Highest State 3-Digit NAICS 31-33 <br/>Average Monthly Employees",
  position = "bottomleft")
```


We might then want to look at how the state HHI index corresponds with its "max" location quotient, which would be the industry in the state that the state has the largest share of, relative to the national average. 

```{r}
state_ind %>% 
  mutate(ind_share_state_sq = ind_share_state**2) %>% 
  group_by(area_fips) %>% 
  reframe(hhi_ind = sum(ind_share_state_sq, na.rm = TRUE), max_ind_lq = max(ind_lq)) %>% 
  left_join(area_codes) %>% 
  filter(!is.na(area_fips)) %>% 
  ggplot() + 
  geom_point(aes(hhi_ind, max_ind_lq), shape = 21, size = 4, color = "black", fill = manf_col, alpha = 0.8) + 
  geom_text_repel(aes(hhi_ind, max_ind_lq, label = state_abbr), max.overlap = 25) + 
  theme_bw() + 
  labs(x = "State Manufacturing GDP by Industry HHI", y = "State Maximum Industry Manufacturing Location Quotient") + 
  axis_theme
```

# 2019 County Data

Note: For now, we will use county employment data to measure the geographical composition of manufacturing across the US. In the future, we will want to change this to GDP data. 

```{r}
county_emp_2019 <- county_emp %>% 
  filter(year == 2019) %>% 
  mutate(COUNTYFP = substr(area_fips, start = 3, stop = str_length(area_fips))) %>% 
  rename(STATEFP = st) %>% 
  filter(disclosure_code != "N")
```

```{r}
county_emp_map_2019 <- left_join(
  county_leaflet %>% 
    mutate(STATEFP = as.numeric(STATEFP)), county_emp_2019
)
```


With our mapping dataset constructed, we start by displaying manufacturing employment levels for each county. 


As before, we want to construct our color palette and label for the map. Fortunately we can use our previous function for colors. 

```{r}
county_cols <- col_def(county_emp_map_2019, emp, brewer.pal(9, "Spectral"))
```

```{r}
county_labels <- sprintf(
  "<strong>%s</strong> <br/> %s <br/> %s <br/> 2019 Average Monthly Employees <br/> <i> NAICS 31-33 </i>",
  county_emp_map_2019$STATE_NAME, county_emp_map_2019$NAME, county_emp_map_2019$emp) %>% lapply(htmltools::HTML)
```


```{r}
county_emp_levels <- county_emp_map_2019 %>% 
  leaflet() %>% 
  setView(-97.59211, 37.91239, zoom = 4) %>% 
  addPolygons(
  fillColor = ~county_cols(county_emp_map_2019$emp),
  weight = 1,
  opacity = 0.5,
  color = "black",
  dashArray = "3",
  fillOpacity = 0.7, 
  highlightOptions = highlightOptions(
    weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 0.7,
    bringToFront = TRUE),
  label = county_labels,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto")) %>% 
  addLegend(pal = county_cols, values = county_emp_map_2019$emp, opacity = 0.7, title = "2019 NAICS 31-33 <br/> Average Monthly Employees",
  position = "bottomleft")

county_emp_levels
```
Having established basic levels, we now turn to investigate the county's share of state employment. 

```{r}
county_2019_share <- county_emp_map_2019 %>% 
  left_join(manf_data %>% filter(year == 2019) %>% select(tot_emp, area_title)) %>% 
  mutate(emp_share = emp/tot_emp, 
         emp_share_perc = emp_share*100,
         emp_share_perc_clean = paste(round(emp_share_perc, 2), "&#37"))
```

Again, we define colors and labels. 


```{r}
county_cols_share <- col_def(county_2019_share, emp_share, brewer.pal(9, "Spectral"))
```

```{r}
county_labels_share <- sprintf(
  "<strong>%s</strong> <br/> %s <br/> %s <br/> 2019 Share of State Employment <br/> <i> NAICS 31-33 </i>",
  county_2019_share$STATE_NAME, county_2019_share$NAME, county_2019_share$emp_share_perc_clean) %>% lapply(htmltools::HTML)
```

```{r}
county_emp_share <- county_2019_share %>% 
  leaflet() %>% 
  setView(-97.59211, 37.91239, zoom = 4) %>% 
  addPolygons(
  fillColor = ~county_cols_share(county_2019_share$emp_share),
  weight = 1,
  opacity = 0.5,
  color = "black",
  dashArray = "3",
  fillOpacity = 0.7, 
  highlightOptions = highlightOptions(
    weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 0.7,
    bringToFront = TRUE),
  label = county_labels_share,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto"))  %>% 
  addLegend(pal = county_cols_share, values = county_2019_share$emp_share, opacity = 0.7, title = "2019 NAICS 31-33 <br/> Share of State Employment",
  position = "bottomleft")

county_emp_share
```

We then display county employment location quotients following the same process as above. 

```{r}
county_cols_lq <- col_def(county_2019_share, lq_emp, brewer.pal(9, "Spectral"))
```

```{r}
county_labels_lq <- sprintf(
  "<strong>%s</strong> <br/> %s <br/> %s <br/> 2019 Employment Location Quotient <br/> <i> NAICS 31-33 </i>",
  county_2019_share$STATE_NAME, county_2019_share$NAME, county_2019_share$lq_emp) %>% lapply(htmltools::HTML)
```


```{r}
county_emp_lq <- county_2019_share %>% 
  leaflet() %>% 
  setView(-97.59211, 37.91239, zoom = 4) %>% 
  addPolygons(
  fillColor = ~county_cols_lq(county_2019_share$lq_emp),
  weight = 1,
  opacity = 0.5,
  color = "black",
  dashArray = "3",
  fillOpacity = 0.7, 
  highlightOptions = highlightOptions(
    weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 0.7,
    bringToFront = TRUE),
  label = county_labels_lq,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto"))  %>% 
  addLegend(pal = county_cols_lq, values = county_2019_share$lq_emp, opacity = 0.7, title = "2019 NAICS 31-33 <br/> Employment Location Quotient",
  position = "bottomleft")

county_emp_lq
```

