---
title: "SEDE Semiconductors"
author: "Nikhil Kalathil"
date: "2024-09-13"
output: html_document
---

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warnings = FALSE)
```

```{r, include = FALSE}
#Libraries
library(tigris)
library(tidyverse)
library(here)
library(leaflet)
library(ggrepel)
library(RColorBrewer)
library(grid)
library(gridExtra)
library(cowplot)
library(readxl)
library(janitor)
library(geofacet)
library(jsonlite)
library(ggridges)
library(sf)
library(here)
library(patchwork)
library(plotly)
library(leaflet.extras)
library(units)
library(jtools)
library(urbnmapr)
library(DescTools)


set.seed(37)
title_theme <- theme(axis.text = element_text(size = 14), 
        axis.title = element_text(size = 18), 
        title = element_text(size = 20))

axis_theme <- theme(axis.text = element_text(size = 10), 
        axis.title = element_text(size = 18), 
         strip.text.x = element_text(size = 16))
```

```{r, include = FALSE}
#Area Crosswalks
area_codes <- readRDS(here("State Data/area_crosswalk.RDS")) %>% 
  mutate(area_title = str_remove(area_title, " -- Statewide")) %>% 
  mutate(area_fips = case_when(
    nchar(area_fips) == 4 ~ paste("0", area_fips, sep = ""), 
    TRUE ~ area_fips
  ))

states <- data.frame(state_abbr = state.abb, area_title = state.name)

area_codes <- left_join(area_codes, states) %>% 
  mutate(state_abbr = case_when(
    area_title == "District of Columbia" ~ "DC",
    area_title == "Puerto Rico" ~ "PR",
    TRUE ~ state_abbr))
```


```{r}
ExpandColorsLIGHT <- function(colors, n, steps = 11){
  if(n <= steps){
    suppressWarnings({
      sapply(colors, function(x){colorRampPalette(c(x, "#FFFFFF"))(steps)}) %>% 
        as.data.frame() %>% 
        filter(row_number() <= n) %>% 
        gather(key = original.color, value = expanded.color)
    })
  }else{
    warning("Select n < steps!")
  }
}
```


```{r}
ExpandColorsDARK <- function(colors, n, steps = 11){
  if(n <= steps){
    suppressWarnings({
      sapply(colors, function(x){colorRampPalette(c(x, "#000000"))(steps)}) %>% 
        as.data.frame() %>% 
        filter(row_number() <= n) %>% 
        gather(key = original.color, value = expanded.color)
    })
  }else{
    warning("Select n < steps!")
  }
}
```

```{r, include = FALSE}
#Map Data
county_sf <- counties(cb = TRUE) %>% 
  shift_geometry(position = "outside")
states_sf <- states(cb = TRUE, resolution = "20m") %>%
  shift_geometry(position = "outside")
```

```{r, include = FALSE}
#Change projection of data for leaflet
states_leaflet <- states_sf %>% 
  sf::st_transform('+proj=longlat +datum=WGS84')

counties_leaflet <- county_sf %>% 
  sf::st_transform('+proj=longlat +datum=WGS84') 
```

```{r, include = FALSE}
#Convert county data to a table
county_data <- counties_leaflet %>% 
  as_tibble() %>% 
  select(STATEFP, COUNTYFP, AFFGEOID) %>% 
  mutate(area_fips = paste(STATEFP, COUNTYFP, sep = ""), 
         st = as.numeric(STATEFP))
```


```{r, include = FALSE}
#Get center of each county
county_centers <- counties_leaflet %>% 
  filter(str_detect(NAME, "Mariana", negate = TRUE)) %>% 
  st_centroid() %>% 
  sf::st_transform('+proj=longlat +datum=WGS84')
```

```{r, include = FALSE}
#Load Existing Data
qcew_3digits <- readRDS(here("State Data/qcew_3digit.RDS")) %>% 
  mutate(industry_desc = substring(industry_title, 11))
```

```{r, include = FALSE}
#Simplify to get industry codes
ind_3digit <- qcew_3digits %>% 
  select(naics_3digit = ind_code, naics_3digit_label = industry_desc) %>% 
  distinct() %>% 
  arrange(naics_3digit_label)
```

```{r, include = FALSE}
#Define colors 
emp_ind_vector <- c(brewer.pal(9, "Greys")[4], "#cf4633", "#BEAED4", "#a8e4a0", "#FDBF6F",  "#386CB0", "#FB8072", brewer.pal(9, "Greys")[3], brewer.pal(9, "Greys")[8], "#80B1D3", "#F0027F",  "#4DAF4A", "#F1E2CC", "#6A3D9A", "#E78AC3", "#CBD5E8", "#666666", brewer.pal(9, "Greys")[5],  brewer.pal(9, "Greys")[6], "#A65628", brewer.pal(9, "Greys")[7])
```

```{r}
#create data frame mapping colors to industries
col_map <- data.frame(ind_3digit$naics_3digit_label, emp_ind_vector)
```

```{r}
rd_col <- data.frame(ind_3digit.naics_3digit_label = "Scientific R&D", emp_ind_vector = "#8DD3C7")
```

```{r}
col_map <- bind_rows(col_map, rd_col)
```


```{r}
# Map 3-digit NAICS to 3-digit Colors
get_col_vec <- function(data){ 
  data %>% 
    select(naics_3digit_label) %>% 
    distinct() %>% 
    unlist()
  }
```

```{r}
#Function to get appropriate 3-digit colors
get_col_match <- function(data){ 
  
 col_vec <- get_col_vec(data)
 
 col_out <- col_map %>% 
   filter(ind_3digit.naics_3digit_label %in% col_vec) %>% 
   select(emp_ind_vector) %>% 
   unlist() %>% 
   unname()
 
  return(col_out)
  
}
```

```{r}
#Get County GEOIDS and crosswalks
cbp_geoid <- read.csv(here("County Data/5_digit_naics_2019.csv")) %>% 
  mutate(area_fips = str_sub(GEO_ID, -5)) %>% 
  select(GEO_ID, NAME, area_fips) %>% distinct()

cbp_empzes <- read.csv(here("County Data/5_digit_naics_2019.csv")) %>% 
  select(EMPSZES_LABEL, EMPSZES) %>% 
  distinct()

cbp_io <- readRDS(here("Input Output Data/cbp_manf_IO_crosswalk.RDS")) 
```


```{r, include = FALSE}
#read county-level manufacturing data
cbp_2019 <- read.csv(here("County Data/6_digit_naics_CBP.csv")) %>% 
  left_join(cbp_geoid) %>% 
  left_join(county_data) %>% 
  left_join(area_codes %>% select(st, state_abbr)) %>% 
  mutate(across(.cols = c(EMP, ESTAB, PAYANN), ~ gsub(",", "", .)),
    emp_num = as.numeric(EMP), 
    ESTAB = as.numeric(ESTAB), 
    mean_pay = as.numeric(PAYANN)
    ) %>% 
  filter(str_detect(NAME, "Mariana", negate = TRUE)) %>% 
  left_join(cbp_empzes)
```


```{r}
cbp_2019_all <- read.csv(here("County Data/total_naics_2019.csv")) %>% 
  mutate(across(.cols = c(EMP, ESTAB, PAYANN), ~ gsub(",", "", .)),
    tot_emp = as.numeric(EMP), 
    tot_estab = as.numeric(ESTAB), 
    tot_mean_earnings = as.numeric(PAYANN)) %>% 
  filter(str_detect(NAME, "Mariana", negate = TRUE), EMPSZES_LABEL == "All establishments") %>%
  select(-c(NAICS2017, NAICS2017_LABEL, LFO_LABEL, EMPSZES_LABEL, ESTAB, PAYANN, EMP))
```

```{r}
cbp_all <- cbp_2019_all %>% select(county_tot_emp = tot_emp, county_tot_estabs = tot_estab, NAME)
```

```{r}
cbp_pay <- cbp_2019 %>% 
  filter(EMPSZES == 1) %>% 
  left_join(cbp_io) %>% 
  ungroup() %>% 
  group_by(ind_code) %>% 
  reframe(ind_mean_pay = mean(mean_pay)) %>% 
  ungroup() 
```


```{r}
#read Input Output Data
use_table_final <- readRDS(here("Input Output Data/use_table_final.RDS"))
sup_com_agg <- readRDS(here("Input Output Data/sup_com_agg.RDS"))
ind_agg <- readRDS(here("Input Output Data/ind_agg.RDS"))
com_agg <- readRDS(here("Input Output Data/com_agg.RDS"))
supply_table_final <- readRDS(here("Input Output Data/supply_table_final.RDS"))
```

```{r}
ind_crosswalk <- readRDS(here("Input Output Data/ind_crosswalk.RDS"))
```



```{r}
#Read NAICS Codes
naics_codes <- read.csv(here("NAICS/naics_codes.csv")) %>% 
  select(c(2,3))

colnames(naics_codes) <- c("industry_code", "industry_desc")
```

```{r, include = FALSE}
naics_2 <- naics_codes %>% 
  filter(str_length(industry_code) == 2 | industry_code == "31-33") %>% 
  mutate(industry_code = case_when(
    industry_code == "31-33" ~ 31.33, 
    TRUE ~ as.numeric(industry_code)
  ))
```

```{r}
naics_sub <- function(var, num){
   as.numeric(str_sub({{ var }}, 1, num))
}
```

```{r}
library(tidycensus)
 us_pop <- get_estimates(geography = "county", product = "population", vintage = 2019)
```


# CBP Data

Direct Codes: 

## Industry Codes


```{r}
semi_naics <- c(334412, 334413, 334416, 334417, 334418, 334419, 333242)
```

## 2019 Data

```{r}
semi_2019_cbp <- cbp_2019 %>% 
  filter(EMPSZES_LABEL == "All establishments",
    NAICS2017 %in% semi_naics) %>% 
  left_join(cbp_2019_all) %>% 
  select(NAICS2017, NAICS2017_LABEL, NAME, emp_num, tot_emp) %>% 
  mutate(emp_share = emp_num / tot_emp) %>% 
  group_by(NAICS2017) %>% 
  mutate(nat_avg_emp = mean(emp_share), 
         LQ_emp = emp_share/nat_avg_emp)
 
```


## 2022 Data 

```{r}
cbp_all_2022 <- read.csv(here("County Data/naics_2022_all.csv")) %>% 
   mutate(across(.cols = c(EMP, ESTAB, PAYANN), ~ as.numeric(gsub(",", "", .)))) %>% 
  select(NAME, YEAR, tot_emp = EMP, tot_estab = ESTAB)
```


```{r}
semi_2022_cbp <- read.csv(here("County Data/semi_naics_2022.csv")) %>% 
   mutate(across(.cols = c(EMP, ESTAB, PAYANN), ~ as.numeric(gsub(",", "", .)))) %>%
  left_join(cbp_all_2022) %>% 
  select(NAICS2017, NAICS2017_LABEL, NAME, emp_num_2022 = EMP, tot_emp_2022 = tot_emp) %>% 
  mutate(emp_share_2022 = emp_num_2022 / tot_emp_2022) %>% 
  group_by(NAICS2017) %>% 
  mutate(nat_avg_emp_2022 = mean(emp_share_2022), 
         LQ_emp_2022 = emp_share_2022/nat_avg_emp_2022)
```


## 2019 Analysis

```{r}
semi_map <- function(industry) { 
  
  semi_2019_cbp %>% 
    filter(NAICS2017 == industry) %>% 
    left_join(counties %>% mutate(NAME = paste(county_name, state_name, sep = ", "))) %>% 
    ggplot(aes(long, lat, group = group)) + 
  geom_polygon(data = urbnmapr::states, colour = "black", fill = "White") + 
  geom_polygon(aes(fill = LQ_emp, text = NAME), color =  "black") +
    guides(fill = "none", color = "none") + 
    scale_fill_distiller(palette = "Spectral") + 
    scale_color_distiller(palette = "Spectral") + 
  theme_map() 
  
}
```

```{r}
get_name <- function(industry){
  
  cbp_2019 %>% 
    filter(NAICS2017 %in% industry) %>% 
    select(NAICS2017_LABEL) %>%
    distinct() %>% 
    mutate(NAICS2017_LABEL = str_remove(NAICS2017_LABEL, " manufacturing")) %>% 
    unlist() %>% 
    unname() 
  
}
```


```{r}
semi_1 <- semi_map(semi_naics[1]) + labs(title = get_name(semi_naics[1]))
semi_2 <- semi_map(semi_naics[2]) + labs(title = get_name(semi_naics[2]))
semi_3 <- semi_map(semi_naics[3]) + labs(title = get_name(semi_naics[3]))
semi_4 <- semi_map(semi_naics[4]) + labs(title = get_name(semi_naics[4]))
semi_5 <- semi_map(semi_naics[5]) + labs(title = get_name(semi_naics[5]))
semi_6 <- semi_map(semi_naics[6]) + labs(title = get_name(semi_naics[6]))
semi_7 <- semi_map(semi_naics[7]) + labs(title = get_name(semi_naics[7]))
```

```{r}
semiconductor_counties <- (semi_2 + semi_5 + semi_1) / (semi_3 + semi_4 + semi_6)
```

```{r}
semi_quad <- (semi_2 + semi_5) / (semi_1 + semi_7)
```

```{r}
semi_quad2 <- semi_3 + semi_4 + semi_6
```

## 2019 - 2022 Change

```{r}
cbp_focus_ind <- c(334418, 334412, 333242, 334413)
```


```{r}
focus_states_tight <- c("ID", "OR", "AZ", "TX", "OH")
```


```{r}
semi_2019_2022 <- semi_2019_cbp %>% 
  full_join(semi_2022_cbp) %>%
  mutate(across(c(emp_num, emp_num_2022, LQ_emp, LQ_emp_2022), ~case_when(
    is.na(.) ~ 0, 
    TRUE ~ .
  ))) %>% 
  mutate(emp_change = (emp_num_2022 - emp_num)/emp_num, 
         LQ_change = (LQ_emp_2022 - LQ_emp ) / LQ_emp) %>% 
  mutate(state = str_extract(NAME, "(?<=, ).*"))
```

```{r}
entry_exit <- semi_2019_2022 %>% 
  left_join(states %>% rename(state = area_title)) %>% 
  filter(NAICS2017 %in% cbp_focus_ind, 
         emp_num == 0 | emp_num_2022 == 0, state_abbr %in% focus_states_tight) %>% 
  mutate(emp_diff = emp_num_2022 - emp_num, emp_sign = emp_diff > 0) %>% 
  ggplot() + 
  geom_col(aes(x = state, y = emp_diff, fill = emp_sign)) + 
  guides(fill = "none") + 
  facet_wrap(~NAICS2017_LABEL) + 
  theme_bw() + 
  labs(x = "State", y = "2019 - 2022 Employment Difference") + 
  axis_theme
```


```{r}
test <- semi_2019_2022 %>% 
  left_join(states %>% rename(state = area_title)) %>% 
  filter(NAICS2017 %in% cbp_focus_ind, state_abbr %in% focus_states_tight) %>% 
  ggplot() + 
  geom_label(aes(x = emp_share, y = emp_change, fill = state_abbr, label = state_abbr), size = 5, show.legend = FALSE, alpha= 0.8) +
  facet_wrap(~NAICS2017_LABEL) + 
  labs(x = "2019 Employment Share", y = "2019-2022 % Change in Employment") + 
  scale_fill_brewer(palette = "Dark2") + 
  theme_bw() + 
  axis_theme + 
  theme(legend.position = "top") + 
  axis_theme
```



# DataAxel Companies

```{r}
semi_axel <- read_xlsx("~/Documents/CMU/Semiconductor_Manufacturing/SemiconductorsDataAxelDataRequest.xlsx")
```

```{r}
semi_companies <- semi_axel %>% 
  select(CONAME, SITE, STADDR, STCITY, STATE, ZIP, STCODE, CNTYCD, CENSUS, BLKGRP, industry_desc = PRMSCD, NAICS_8 = NAICS) %>% 
  mutate(NAICS_6 = str_sub(NAICS_8, 1, 6))
  
```

```{r}
focus_states <- c("ID", "OR", "AZ", "TX", "FL", "OH")
```


```{r}
defense_states <- c("CA", "AZ", "MA", "NM", "FL", "GA", "MI", "OH")
```

```{r}
semi_naics <- c(334412, 334413, 334416, 334417, 334418, 334419, 333242)
```

```{r}
semi_focus <- c(33441302, 33441303, 33441801, 33441203, 33324201, 33441202)
```

```{r}
semi_focus_tight <- c(33441302, 33441303, 33324201)
```

```{r}
semi_companies %>% 
  filter(STATE %in% focus_states_tight, 
         NAICS_8 %in% semi_focus_tight) %>% 
  mutate(NAICS_8 = factor(NAICS_8, levels = c(33324201, 33441302, 33441303))) %>% 
  group_by(industry_desc, STATE) %>% 
  count() %>% 
  ggplot() + 
  geom_col(aes(x = reorder(STATE, n), y  = n, fill = reorder(industry_desc, n)), color = "black") + 
  coord_flip() + 
  theme_bw() + 
  labs(x = "State", y = "Semiconductor Industry")
```

# Bloomberg Data

```{r}
semi_bm <- read.csv("~/Documents/CMU/Semiconductor_Manufacturing/fabs_in_states.csv")
```

```{r}
fab_hetero <- semi_bm %>% group_by(State.Province, FabType) %>% count() %>% ggplot() + geom_col(aes(x = n, y = reorder(State.Province, n), fill = FabType), color = "Black") + scale_fill_brewer(palette = "Spectral") + theme_bw() + labs(x = "Number of Facilities", y = "") + axis_theme
```

```{r}
semi_bm %>% group_by(State.Province, I.C.) %>% count() %>% ggplot() + geom_col(aes(x = n, y = State.Province, fill = I.C.))
```

```{r}
semi_bm %>% filter(!is.na(Planned.or.Curr.Geom..μm.))  %>% 
  ggplot() +
  geom_density_ridges2(aes(x = Planned.or.Curr.Geom..μm., y = State.Province ))
```

```{r}
semi_bm %>% filter(!is.na(Planned.or.Curr.Geom..μm.))  %>% 
  group_by(State.Province, Planned.or.Curr.Geom..μm.) %>% 
  count() %>% 
  ggplot() +
  geom_point(aes(x = Planned.or.Curr.Geom..μm., y = n, color = State.Province)) + 
  facet_wrap(~State.Province)
```
# Sketching out the analysis

How do the R&D, import / exporting, and establishment level charactersitics of the semiconductor industry vary across regions? 

3 Data sources: 
- US CBP / IO Accounts (employment, establishments), (agglomeration)
- Semi data (fab wafer size, fab type, fab products)
- DataAxel data (semiconductor company names)

## Read Agglomeration Data

```{r}
semi_agg <- readRDS(here("semi_agg.RDS")) %>% 
  filter(NAICS2017 == "334413")
```

## Get Other Data and Match

Start by matching company names across DataAxel and the bloomberg data.

```{r}
semi_focus_core <- c(33441302, 33441303)
```

```{r}
semi_bm_clean <- semi_bm %>% 
  select(company = X, city = City, state_name = State.Province, fab_name = Fab.Name, 5, 6, curr_geom = Planned.or.Curr.Geom..μm., fab_capacity = Fab.Capacity..200mm.Equiv., Origin, address = Address, Zip, Website, Probability, Status, project_type = Project.Type, product_type = Prod.Type, prod_type_2 = Product.Type..2., products = Products, tech = Technology, class = I.C., waf_size = Planned.or.Curr.Wafsiz, capacity = Planned.or.Curr.Full.Cap., start_year = Start.Year.Initial, fac_type = Project.Type.Core, notes = Fab.Comment) %>% 
  filter(company != "") %>% 
  filter(start_year < 2023)
```

```{r}
semi_companies_clean <- semi_companies %>% 
  select(company = CONAME, address = STADDR, city = STCITY, state_abbr = STATE, Zip = ZIP, state_fips = STCODE, county_fips = CNTYCD, census_tract = CENSUS, industry_desc, NAICS_8, NAICS_6) %>% 
  filter(state_abbr %in% focus_states)
```

```{r}
semi_bm_clean %>% 
  group_by(company, city, state_name, address) %>% 
  count() %>% 
  view()
```


```{r}
semi_companies_match <- semi_companies_clean[3]
```

```{r}
find_comp <- function(i, data){
  
  df <- data
  
  co_name <- df$company[i] 
  
  city_name <- df$city[i]
  
  df_store <- semi_companies_clean %>% 
    filter(str_detect(city, city_name)) %>% 
    mutate(co_match = case_when(
      str_detect(tolower(company), tolower(co_name)) ~ 1
    )) %>% 
    select(co_match, everything()) %>%
    filter(co_match == 1)

  
  if (nrow(df_store) == 0) { 
    return(co_name)}
  
  else { 
    return(df_store)}

}
```


```{r}
unmatched_co <- c()
```


```{r}
for (i in 1:nrow(semi_bm_clean)){

  if (typeof(find_comp(i, semi_bm_clean)) == "character"){
    
    unmatched_co <- append(unmatched_co, find_comp(i, semi_bm_clean))
    
  } 
  
  
  if (typeof(find_comp(i)) == "list"){
    
    semi_companies_match <- semi_companies_match %>% bind_rows(find_comp(i, semi_bm_clean)) %>% filter(!is.na(company))
    
  } 
  
}
```


```{r}
semi_bm_clean %>% filter(company %in% unmatched_co) %>% 
  mutate(company = case_when(
    company == "Entrepix Inc." ~ "Entrepix",
    company == "Lasertel Inc." ~ "Lazer Tel Inc",
    company == "Panjit International" ~ "Pan Jit Americas Inc", 
    company == "Qorvo Inc." ~ "Qorvo Inc", 
    company == "X-FAB Silicon Foundries" ~ "X-Fab Texas Inc"
    
    TRUE ~ company
  ), 
  city = case_when(
    company %in% c("Entrepix", "Microchip") & city == "Tempe" ~ "Phoenix", 
    company %in% c("ON Semiconductor Corp") & city == "Meridian" ~ "Nampa"
    TRUE ~ city
  ))
```


## Geolocating Data

We then begin the process of geocoding. We will use [Google's geolocating service](https://developers.google.com/maps/documentation/geocoding/intro) to process our geolocation requests. To use this service, we need to get an [API key](https://developers.google.com/maps/documentation/geocoding/get-api-key)

```{r, echo = FALSE, Include = FALSE}
api_key <- c("KEY")
```

We define our function, which will take an address as an input and output a latitude and longitude result. 

```{r}
# Function to extract county name
extract_county <- function(json_obj) {
  # Check for county within address_components
  county <- json_obj$results[[1]]$address_components %>%
    purrr::map_chr(~ .x$long_name) %>%
   grep("County", ., value = TRUE)
  
  return(county)

}
```

```{r}
geocodeAddress <- function(address) {
  require(RJSONIO)
  url <- "https://maps.googleapis.com/maps/api/geocode/json?address="
  url <- URLencode(paste(url, address, sep = ""))
  url <- URLencode(paste(url, "&key=", api_key, sep = ""))
  x <- fromJSON(url, simplify = FALSE)
  print(x$status)
  if (x$status == "OK") {
    out <- c(x$results[[1]]$geometry$location$lng,
             x$results[[1]]$geometry$location$lat,
             x$results[[1]]$formatted_address, 
             extract_county(x))
  } else {
    out <- NA
  }
  Sys.sleep(0.2)  # API only allows 5 requests per second
  out
}
```

We now clean and prepare our data for geocoding. 

```{r}
semi_bm_final <- semi_bm_clean %>% 
    mutate(company = case_when(
      company == "Entrepix Inc." ~ "Entrepix",
      company == "Lasertel Inc." ~ "Lazer Tel Inc",
      company == "Panjit International" ~ "Pan Jit Americas Inc", 
      company == "Qorvo Inc." ~ "Qorvo Inc", 
      company == "X-FAB Silicon Foundries" ~ "X-Fab Texas Inc",
      TRUE ~ company
    ), 
    city = case_when(
      company %in% c("Entrepix", "Microchip") & city == "Tempe" ~ "Phoenix", 
      company %in% c("ON Semiconductor Corp") & city == "Meridian" ~ "Nampa",
      TRUE ~ city), 
    location = paste(company, address, city, state_name, sep = ", "))
```

Now we loop through the addresses to get the latitude and longitude of each address and add it to the original address data frame in the  new columns lat and long. 

```{r}
origAddress <- semi_bm_final %>% 
  distinct(company, location, state_name)
```


```{r, include = FALSE}
for(i in 1:nrow(origAddress))
{
  result <- geocodeAddress(origAddress$location[i])
  origAddress$long[i] <- as.numeric(result[1])
  origAddress$lat[i] <- as.numeric(result[2])
  origAddress$form_address[i] <- as.character(result[3])
  origAddress$county[i] <- as.character(result[4])
}
```

```{r}
origAddress$county[56] <- "Dallas County"
```

```{r}
county_crosswalk <- counties %>% select(county_name, area_fips = county_fips, state_fips, state_abbr = state_abbv, state_name) %>% distinct() %>% mutate(area_fips = as.numeric(area_fips))
```


```{r}
semi_bm_location <- origAddress %>% 
  rename(county_name = county) %>% 
  left_join(county_crosswalk) %>% 
  left_join(semi_bm_final, .)
```

```{r}
semi_da_location <- semi_companies_clean %>% mutate(area_fips = state_fips*1000 + county_fips) %>% select(-c(state_fips)) %>% 
  left_join(county_crosswalk)
```

## Final Match

```{r}
matched_co <- c()
```


```{r}
unmatched_co <- c()
```

```{r}
semi_companies_match <- semi_companies_clean[3]
```

```{r}
for (i in 1:nrow(semi_bm_location)){

  if (typeof(find_comp(i, semi_bm_location)) == "character"){
    
    unmatched_co <- append(unmatched_co, find_comp(i, semi_bm_location))
    
  } 
  
  
  if (typeof(find_comp(i, semi_bm_location)) == "list"){
    
    matched_co <-  append(matched_co, find_comp(i, semi_bm_location) %>% select(company) %>% distinct() %>% unlist() %>% unname())
    
    semi_companies_match <- semi_companies_match %>% bind_rows(find_comp(i, semi_bm_location)) %>% filter(!is.na(company))
    
  } 
  
}
```

```{r}
semi_bm_location %>% 
saveRDS(here("bm_geocoded.RDS"))
```

## Final Measures

```{r}
bm_stats <- semi_bm_location %>% 
  mutate(geom_cat = case_when(
    curr_geom <= 0.007 ~ "Leading Edge", 
    curr_geom > 0.007 & curr_geom <= 0.014 ~ "Advanced Capabilities", 
    curr_geom > 0.014 & curr_geom <= 0.026 ~ "Cost Optimal", 
    curr_geom > 0.026 & curr_geom <= 0.090 ~ "Mature", 
    curr_geom > 0.090 ~ "Legacy"
  ), matched = company %in% matched_co) %>% 
  group_by(area_fips, county_name, state_name, FabType, geom_cat, curr_geom, company) %>%
  reframe(n_fab = n(), matched_fab = sum(as.numeric(matched)))
```

```{r}
comp_stats <- semi_da_location %>% 
  mutate(matched = company %in% matched_co) %>% 
  group_by(area_fips, county_name, state_name) %>% 
  reframe(n_comps = n(), matched_comps = sum(as.numeric(matched)))
```

## Join with agglomeration data 

```{r}
semi_agg_sum <- semi_agg %>% 
  select(NAME, state_abbr, horz_z, vert_z) %>% 
  separate(NAME, into = c("county_name", "state_name"), sep = ", ", remove = FALSE)
```

```{r}
focus_counties <- c("Maricopa County, Arizona", "Washington County, Oregon", "Dallas County, Texas", "Ada County, Idaho", "Lucas County, Ohio", "Broward County, Florida")
```

```{r}
agg_measures <- semi_agg_sum %>% 
  filter(NAME %in% focus_counties) %>% 
  ggplot() + 
  geom_point(aes(x = horz_z, y = vert_z, label = NAME, color = state_abbr)) + 
  guides(color = "none") + 
  geom_label_repel(aes(x = horz_z, y = vert_z, label = NAME)) + 
  geom_vline(xintercept = 0) + 
  geom_hline(yintercept = 0) + 
  labs(x = "Horizontal (Peer) Agglomeration \nEmployment, County X Industry", y = "Vertical (Supply-Chain) Agglomeration \nEmployment, County X Industry", shape = "")  + 
  theme_bw() + 
  axis_theme
```

```{r}
geom_graph <- bm_stats %>% 
  filter(!is.na(geom_cat)) %>% 
  mutate(NAME = paste(county_name, state_name, sep = ", ")) %>% 
  group_by(curr_geom, NAME, geom_cat) %>% 
  reframe(n_geom = sum(n_fab)) %>% 
  left_join(semi_agg_sum) %>% 
  filter(!is.na(horz_z), NAME %in% focus_counties) %>% 
  mutate(order = case_when(geom_cat == "Legacy" ~ 5, geom_cat == "Mature" ~ 4, geom_cat == "Cost Optimal" ~ 3, geom_cat == "Advanced Capabilities" ~ 2, geom_cat == "Leading Edge" ~ 1)) %>% 
  ggplot() + 
  geom_point(aes(x = reorder(NAME, horz_z), y = factor(curr_geom), fill = geom_cat, size = n_geom), shape = 22) + 
  geom_text(aes(x = reorder(NAME, horz_z), y = factor(curr_geom), label = n_geom)) + 
  scale_fill_brewer(palette = "BrBG") +
  scale_size_continuous(range = c(10, 13)) + 
  guides(size = "none", fill = "none") + 
  labs(x ="", y = "Geometry") + 
  theme_bw() + 
  axis_theme + 
  theme(axis.text.x = element_text(size = 18))
```

```{r}
comp_info <- bm_stats %>% 
  filter(!is.na(geom_cat)) %>% 
  mutate(NAME = paste(county_name, state_name, sep = ", ")) %>% 
  group_by(curr_geom, FabType, NAME, company, geom_cat) %>% 
  reframe(n_geom = sum(n_fab)) %>% 
  mutate(rd_fab = case_when(
    str_detect(FabType, "Fab") ~ "Fab", 
    str_detect(FabType, "R&D") ~ "R&D"
  )) %>% 
  left_join(semi_agg_sum) %>% 
  filter(!is.na(horz_z), NAME %in% focus_counties) 
```

```{r}
fab_geom <- geom_graph + 
  geom_label_repel(data = comp_info, aes(x = reorder(NAME, horz_z), y = factor(curr_geom), label = paste(rd_fab, sep = " -- "), fill = geom_cat, alpha = rd_fab), size = 6) + 
  scale_alpha_discrete(range = c(0.5, 0.9)) 
```

```{r}
"#FFFFFF" "#F0F0F0" "#D9D9D9" "#BDBDBD" "#969696" "#737373" "#525252" "#252525" "#000000"
```


```{r}
test <- geom_graph + 
  ggnewscale::new_scale_fill() + 
  geom_text_repel(data = comp_info, aes(x = reorder(NAME, horz_z), y = factor(curr_geom), label = paste(company, rd_fab, sep = " -- "), alpha = rd_fab), size = 6) + 
  scale_alpha_discrete(range = c(0.6, 0.8)) 
```




```{r}
fab_geom_col <- bm_stats %>% 
  filter(!is.na(geom_cat)) %>% 
  mutate(NAME = paste(county_name, state_name, sep = ", ")) %>% 
  group_by(curr_geom, FabType, NAME, company) %>% 
  reframe(n_geom = sum(n_fab)) %>% 
  left_join(semi_agg_sum) %>% 
  filter(!is.na(horz_z), NAME %in% focus_counties) %>% 
  ggplot() + 
  geom_point(aes(x = reorder(NAME, horz_z), y = factor(curr_geom), fill = factor(FabType, levels = c("CMP", "Fab & Backend", "Fab, BEOL", "Fab/EPI", "Fab", "Fab, Pilot", "Fab, Pilot, R&D", "Fab, R&D" , "Pilot", "R&D", "R&D, Pilot")), size = n_geom), shape = 22) + 
  geom_label_repel(aes(x = reorder(NAME, horz_z), y = factor(curr_geom), fill = factor(FabType, levels = c("CMP", "Fab & Backend", "Fab, BEOL", "Fab/EPI", "Fab", "Fab, Pilot", "Fab, Pilot, R&D", "Fab, R&D" , "Pilot", "R&D", "R&D, Pilot")), label = paste(FabType, sep = " -- ")), size = 6) + 
  scale_fill_brewer(palette = "Spectral") +
  scale_size_continuous(range = c(10, 13)) + 
  guides(fill = "none", size = "none") + 
  labs(x ="", y = "Geometry") + 
  theme_bw() + 
  axis_theme + 
  theme(axis.text.x = element_text(size = 18))
```

```{r}
fab_geom_company <- bm_stats %>% 
  filter(!is.na(geom_cat)) %>% 
  mutate(NAME = paste(county_name, state_name, sep = ", ")) %>% 
  group_by(curr_geom, FabType, NAME, company) %>% 
  reframe(n_geom = sum(n_fab)) %>% 
  left_join(semi_agg_sum) %>% 
  filter(!is.na(horz_z), NAME %in% focus_counties) %>% 
  ggplot() + 
  geom_point(aes(x = reorder(NAME, horz_z), y = factor(curr_geom), fill = factor(FabType, levels = c("CMP", "Fab & Backend", "Fab, BEOL", "Fab/EPI", "Fab", "Fab, Pilot", "Fab, Pilot, R&D", "Fab, R&D" , "Pilot", "R&D", "R&D, Pilot")), size = n_geom), shape = 22) + 
  geom_label_repel(aes(x = reorder(NAME, horz_z), y = factor(curr_geom), fill = factor(FabType, levels = c("CMP", "Fab & Backend", "Fab, BEOL", "Fab/EPI", "Fab", "Fab, Pilot", "Fab, Pilot, R&D", "Fab, R&D" , "Pilot", "R&D", "R&D, Pilot")), label = paste(company, FabType, sep = " -- ")), size = 6) + 
  scale_fill_brewer(palette = "Spectral") +
  scale_size_continuous(range = c(10, 13)) + 
  guides(fill = "none", size = "none") + 
  labs(x ="", y = "Geometry") + 
  theme_bw() + 
  axis_theme + 
  theme(axis.text.x = element_text(size = 18))
```



```{r}
geom_stats <- bm_stats %>% 
  filter(!is.na(geom_cat)) %>% 
  group_by(curr_geom, area_fips, county_name, state_name, geom_cat) %>% 
  reframe(n = sum(n_fab), matched_fab = sum(matched_fab)) %>% 
  mutate(NAME = paste(county_name, state_name, sep = ", "),
         order = case_when(geom_cat == "Legacy" ~ 5, geom_cat == "Mature" ~ 4, geom_cat == "Cost Optimal" ~ 3, geom_cat == "Advanced Capabilities" ~ 2, geom_cat == "Leading Edge" ~ 1)) %>% 
  left_join(semi_agg_sum) %>% 
  filter(!is.na(horz_z), NAME %in% focus_counties) %>% 
  ggplot() + 
  geom_col(aes(x = reorder(NAME, horz_z), y = n, fill = factor(curr_geom), group = "NAME"), color = "black", position = "stack") + 
  geom_label(aes(x = reorder(NAME, horz_z), y = n, fill = factor(curr_geom), label = curr_geom, group = "NAME"), color = "black", position = "stack") + 
  scale_fill_manual(values = c(brewer.pal(12, "Spectral"), brewer.pal(9, "BuPu")[5:9])) +  
  labs(x = "", y = "Number of Facilities") + 
  guides(fill = "none") + 
  theme_bw() + 
  axis_theme
```

```{r}
fab_stats <- bm_stats %>% 
  filter(!is.na(FabType)) %>% 
  group_by(FabType, area_fips, county_name, state_name) %>% 
  reframe(n = sum(n_fab), matched_fab = sum(matched_fab)) %>% 
  mutate(NAME = paste(county_name, state_name, sep = ", ")) %>% 
  left_join(semi_agg_sum) %>% 
  filter(!is.na(horz_z), NAME %in% focus_counties) %>% 
  ggplot() + 
  geom_col(aes(x = reorder(NAME, horz_z), y = n, fill = factor(FabType, levels = c("CMP", "Fab & Backend", "Fab, BEOL", "Fab/EPI", "Fab", "Fab, Pilot", "Fab, Pilot, R&D", "Fab, R&D" , "Pilot", "R&D", "R&D, Pilot"))), color = "Black") + 
  scale_fill_brewer(palette = "Spectral") + 
  labs(x = "", y = "Number of Facilities", fill = "Fab Type") + 
  theme_bw() + 
  axis_theme
```


```{r}
firm_stats <- comp_stats %>% 
  mutate(NAME = paste(county_name, state_name, sep = ", ")) %>% 
  left_join(semi_agg_sum) %>% 
  filter(!is.na(horz_z), NAME %in% focus_counties) %>% 
  ggplot() + 
  geom_col(aes(x = reorder(NAME, horz_z), y = n_comps)) + 
  geom_col(aes(x = reorder(NAME, horz_z), y = matched_comps), fill = "forest green") + 
  theme_bw() + 
  labs(x = "", y = "Number of Companies") + 
  axis_theme
```

