---
title: "NCSL Cleaning"
author: "Nikhil Kalathil"
date: "2023-05-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include == FALSE }
library(tidyverse)
library(tidytext)
library(RColorBrewer)
library(ggthemes)
library(here)
library(ggrepel)
library(lubridate)
library(ggnewscale)
library(readxl)
library(patchwork)
#library(htmltools)
#library(htmlwidgets)
#library(RJSONIO)
```


```{r}
title_theme <- theme(axis.text = element_text(size = 14), 
        axis.title = element_text(size = 18), 
        title = element_text(size = 20))

axis_theme <- theme(axis.text = element_text(size = 10), 
        axis.title = element_text(size = 18))
```

This document cleans and summarizes the NCSL State Action on Coronavirus Relief Funds database, that was previously webscraped and then manually edited in excel. 

# Bring in Data

```{r}
ncsl_raw <- read_csv(here("Webscraping/ncsl.csv"))
```
Our first task is to try and split the description variable into parts, extracting a total dollar amount, and separating out the project description. 

To do this, we will extract information between the dollar sign, and the next space. This should capture all of the dollar amount information we want. We drop one observation that adds redundant information in Missouri. 

```{r}
ncsl_clean <- ncsl_raw %>% 
  mutate(dollars_raw = str_remove(str_extract(Description, "\\$.*?\\s"), "\\$"), 
         million_mark = str_detect(Description, "million"),
         billion_mark = str_detect(Description, "billion"),
         description_clean = str_remove(Description, "\\$.*?\\s"),
         description_clean = str_remove(description_clean, "million to"), 
         description_clean = str_remove(description_clean, "million"), 
         description_clean = str_remove(description_clean, "in|for|a|to"),
         description_clean = str_trim(description_clean), 
         dollars_spent = as.numeric(gsub(",", "", dollars_raw)), 
         dollars_spent = case_when(
           million_mark == TRUE ~ dollars_spent * 1000000, 
           billion_mark == TRUE ~ dollars_spent * 1000000000,
           TRUE ~ dollars_spent
         ), 
         dollars_spent = case_when(
           dollars_spent < 500 ~ dollars_spent * 1000000, 
           TRUE ~ dollars_spent
         ), 
         drop = case_when(
           State == "Missouri" & str_detect(Description, "billion") ~ 1
         )
         ) %>%
  filter(is.na(drop)) %>% 
  select(State, Category, Description, dollars_spent, description_clean, Source) %>% 
  filter(!is.na(dollars_spent))
```


We can now get some quick summary statistics and plot against the size of the state's economy. 

```{r}
ncsl_category <- ncsl_clean %>% 
  group_by(State, Category) %>% 
  summarize(total_dollars = sum(dollars_spent))
```

```{r}
ncsl_state <- ncsl_clean %>% 
  group_by(State) %>% 
  summarize(total_dollars = sum(dollars_spent))
```

# Pandemic Oversight CRF Data

In addition, we were able to find a new, far more detailed database of state use of CRF. These data are taken from a government website, [Pandemic Oversight](https://www.pandemicoversight.gov/data-interactive-tools/interactive-dashboards/coronavirus-relief-fund), which provides a detailed breakdown of specific awards related to the Coronavirus Relief Fund. 

We start by importing and cleaning data frames, beginning with a state overview. 

```{r}
project_details <- read.csv(here("CRF/Project Details.csv"))
```

```{r}
crf_payments <- read_xlsx(here("CRF/crf_payments.xlsx"))
```

```{r}
crf_payments %>% 
  filter(!is.na(Amount)) %>% 
  filter(str_detect(State_Local, "Payment to |Total allocation", negate = TRUE)) %>% 
    view()
```



```{r}
ppe_projects <- project_details %>% 
  filter(str_detect(Project.description, "PPE")) %>% 
  group_by(Sub.recipient, Award.number) %>% 
  reframe(award_dollars = sum(Sub.award.amount), spent_dollars = sum(Money.spent.to.date), Project.description, Award.description, Spending.category) %>% 
  filter(str_detect(Spending.category, "Select", negate = TRUE))
```


```{r}
ppe_projects %>% 
  group_by(Spending.category) %>% 
  count()
```

```{r}
token_list_broad <- c("Unemployment Benefits", "facilitate Distance Learning", "Food Programs", "Housing Support", "Improve Telework Capabilites of Public Employees")
```

```{r}
ppe_projects_short <- ppe_projects %>% 
  filter(!Spending.category %in% token_list_broad)
```


Bring in mask data to check against. 

```{r}
box_dir <- "/Users/Nosheal/Library/CloudStorage/Box-Box/COVID 19 Master Folder/Data/Masks/"
```

```{r}
box_here <- function(file) { 
  paste(box_dir, file, sep = "")
  }
```


```{r}
mask_sample <- readRDS(box_here("final_sample.RDS"))
```

```{r}
mask_sample %>% 
  mutate(corp_category = case_when(
    `date founded` < 2020 ~ "Diversifying", 
    `date founded` >= 2020 ~ "De_Novo"
  )) %>% 
  mutate(corp_cateogry = case_when(
    fda_incumbent == 1 | niosh_incumbent == 1 ~ "Incumbent", 
    is.na(`date founded`) ~ "Unknown", 
    TRUE ~ corp_category
  ))
```

```{r}
remove <- c("Limited" ,"Ltd", "LTD", "Incorporated", "Company",  "Corporation", "Co", "Inc",  "[[:punct:]]", "LLC", "INC")
```


```{r}
mask_comps <- mask_sample %>% 
  select(dom_useful_num, original_company_name) %>% 
    mutate(comp_match = tolower(str_trim(str_remove_all(original_company_name, paste(remove, collapse = "|")))))
```

```{r}
ppe_projects_short %>% 
  select(Sub.recipient) %>% 
  distinct() %>% 
  mutate(comp_match = tolower(str_trim(str_remove_all(Sub.recipient, paste(remove, collapse = "|"))))) %>% 
  left_join(mask_comps) %>% 
  view()
  
```

~  15/3000 matches 

## QCEW Data 

```{r}
qcew_state <- readRDS(here("State Data/qcew_state.RDS"))
```

```{r}
qcew_prelim <- qcew_state %>% 
  filter(year == 2020, industry_code == "31-33") %>% 
  select(area_fips, estabs, tot_estabs, emp, tot_emp, lq_estabs, lq_wages, lq_emp) %>% 
  mutate(manf_share = estabs / tot_estabs, 
         manf_emp_share = emp / tot_emp)
```

```{r}
area_codes <- readRDS(here("State Data/area_crosswalk.RDS")) %>% 
  mutate(area_title = str_remove(area_title, " -- Statewide")) %>% 
  mutate(area_fips = case_when(
    nchar(area_fips) == 4 ~ paste("0", area_fips, sep = ""), 
    TRUE ~ area_fips
  ))
```


```{r}
states <- data.frame(state_abbr = state.abb, area_title = state.name)
```

```{r}
qcew_states <- area_codes %>% 
  left_join(states) %>% 
  left_join(qcew_prelim, .)
```

# GDP Data

```{r}
state_gdp <- readRDS(here("State Data/state_gdp.RDS")) %>% 
  filter(GeoName != "United States") %>% 
  mutate(year = as.numeric(year))
```

```{r}
col1 <- brewer.pal(8, "Set2")[3]
```

```{r}
ncsl_gdp_totals <- state_gdp %>% 
  filter(year == 2020) %>% 
  select(State = GeoName, state_gdp) %>% 
  left_join(ncsl_state, . ) %>%  
  left_join(states %>% rename(State = area_title)) %>% 
  ggplot() + 
  geom_point(aes(x = state_gdp, y = total_dollars), shape = 21, fill = col1, size = 3, color = "black", alpha = 0.8) + 
  #geom_text(aes(x = state_gdp + 50000, y = total_dollars, label = state_abbr)) + 
  scale_x_continuous(labels = scales::unit_format(unit = "$B", scale = 1e-3)) + 
  scale_y_continuous(labels = scales::unit_format(unit = "$B", scale = 1e-9)) + 
  theme_bw() +
  labs(x = "State GDP in 2020 (Billions of $)", y = "Federal CARES Act Funding Spent \n(Billions of $)") +
  title_theme + 
  axis_theme
```


```{r}
state_sum_1_emp <- qcew_states %>% 
  select(State = area_title, tot_emp, emp, state_abbr) %>% 
  left_join(ncsl_state, .) %>% 
  ggplot() + 
  geom_point(aes(x = tot_emp, y = total_dollars), shape = 21, fill = col1, size = 3, color = "black", alpha = 0.8) + 
  geom_text(aes(x = tot_emp + 100000, y = total_dollars, label = state_abbr)) + 
  scale_x_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6)) + 
  scale_y_continuous(labels = scales::unit_format(unit = "$B", scale = 1e-3)) + 
  theme_bw() +
  labs(x = "Total Employees in 2020", y = "Federal CARES Act Funding Spent \n(Billions of $)") +
  title_theme + 
  axis_theme
```



```{r}
state_sum_2 <- qcew_states %>% 
  select(State = area_title, tot_emp, emp, state_abbr) %>% 
  left_join(ncsl_state, .) %>% 
  ggplot() + 
  geom_point(aes(x = emp, y = total_dollars), shape = 21, fill = col1, size = 3, color = "black", alpha = 0.8) + 
  geom_text(aes(x = emp + 10000, y = total_dollars, label = state_abbr)) + 
  scale_x_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6)) + 
  scale_y_continuous(labels = scales::unit_format(unit = "$B", scale = 1e-9)) + 
  theme_bw() +
  labs(x = "Total Manufacturing Employees in 2020", y = "Federal CARES Act Funding Spent \n(Billions of $)") +
  title_theme + 
  axis_theme
```

```{r}
col2 <- c(brewer.pal(8, "Set2"), brewer.pal(8, "Set3")[1:4])
```




```{r}
state_sum_3 <- qcew_states %>% 
  select(State = area_title, state_abbr) %>% 
  left_join(ncsl_category, .) %>% 
  group_by(State) %>% 
  mutate(state_total = sum(total_dollars)) %>% 
  ungroup() %>% 
  mutate(percent_spent = total_dollars/state_total) %>% 
  ggplot() + 
  geom_col(aes(x = reorder(state_abbr, -state_total), y = percent_spent, fill = Category, group = Category), color = "black", alpha = 0.8) + 
  scale_fill_manual(values = col2)  + 
  scale_y_continuous(labels = scales::percent) +
  theme_bw() + 
  labs(x = "State", y = "Percent of Federal CARES Funding Spent by Category", fill = "Spending Category") + 
  title_theme + 
  axis_theme + 
  theme(legend.text = element_text(size = 14), 
        axis.text.x = element_text(angle = 90)) 
```
```

